---
title: "Bihar Network Analysis"
author: "Ethan Berman"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = F, warning = F, message = F, results = 'asis'}

#####################################
###SET FILE LOCATIONS TO RUN CODE####
#####################################

# ego igraph file
ego_igraph_f <- "/Users/bermane/Team Braintree Dropbox/Ethan Berman/R Projects/icrw-egocentric-analysis/data/ego_igraph.rda"

# combined igraph file
combined_igraph_f <- "/Users/bermane/Team Braintree Dropbox/Ethan Berman/R Projects/icrw-egocentric-analysis/data/combined_igraph.rda"

# alter igraph file
alter_igraph_f <- "/Users/bermane/Team Braintree Dropbox/Ethan Berman/R Projects/icrw-egocentric-analysis/data/alter_igraph.rda"

# ego data file
ego_data_f <- "/Users/bermane/Team Braintree Dropbox/Ethan Berman/R Projects/icrw-egocentric-analysis/data/ego_clean_complete_11012022.xlsx"

# alter data file
alter_data_f <- "/Users/bermane/Team Braintree Dropbox/Ethan Berman/R Projects/icrw-egocentric-analysis/data/alter_clean_complete_11012022.xlsx"

# ego pc data file
ego_pc_f <- "data/ego_pc_complete_12012022.xlsx"

# duplicate id file
dup_id_f <- 'data/duplicate_ids_02022022.xlsx'

```

# 1. Centrality and Density Measures
## A) Ego Metrics

```{r, echo = F, warning = F, message = F, results = 'asis'}
# this code loads network objects for ego and alter and generates network metrics
# and related figures

# load packages
library(tidyverse)
library(igraph)
library(ggraph)
library(janitor)
library(magrittr)
library(kableExtra)

#######################################
### EGO NETWORK DATA BASIC METRICS ####
#######################################

# load ego igraph objects
load(ego_igraph_f)

# measures based on ego
ego_ego_met <- gr_list_ego %>%
  map_dfr(~ tibble(deg = degree(.x, v = 'ego'),
                   bet = betweenness(.x, v = 'ego', weights = NA),
                   clo = closeness(.x, v = 'ego', weights = NA)),
          .id = 'ego_id')

# print ego degree centrality table
ego_ego_met %>% tabyl(deg) %>% round(2) %>%
  rename(degree = deg) %>%
  kbl(caption = 'Ego Degree Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# print ego betweeness centrality table
ego_ego_met %>% tabyl(bet) %>% round(2) %>%
  rename(betweenness = bet) %>%
  kbl(caption = 'Ego Betweenness Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# print ego closeness table
ego_ego_met %>% tabyl(clo) %>% round(2) %>%
  rename(closeness = clo) %>%
  kbl(caption = 'Ego Closeness Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# sort ego_df and ego_ego_met by ego_id
ego_ego_met %<>% arrange(ego_id)
ego_df %<>% arrange(ego_id)

# make sure ego_ids match
# sum(ego_ego_met$ego_id == ego_df$ego_id)
  
# add district, block, age, education, caste, parity, husband migrant columns to ego_ego_met
ego_ego_met %<>% add_column(geography = ego_df$geography,
                            district = ego_df$district_name,
                            block = ego_df$block_name,
                            age = ego_df$ego_age,
                            edu = ego_df$ego_edu,
                            caste = ego_df$ego_caste,
                            parity = ego_df$ego_parity,
                            husband_migrant = ego_df$ego_hus_mig,
                            ever_worked = ego_df$ego_ever_worked,
                            worked_last_year = ego_df$ego_worked_lastyr)

# calculate degree centrality by ego age
# two groups, 18-21 and 22-24
ego_ego_met %>%
  select(deg, age) %>%
  rename(degree = deg) %>%
  mutate(age = case_when(age <= 21 ~ '18-21',
                         age > 21 ~ '22-24')) %>%
  tabyl(age, degree) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top') %>%
  kbl(caption = 'Ego Degree Centrality by Age (pcq102)') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# calculate degree centrality by ego parity
# NA, 0, 1, 2

# set NA values to 0
ego_ego_met$parity[is.na(ego_ego_met$parity)] <- 0

ego_ego_met %>%
  select(deg, parity) %>%
  rename(degree = deg) %>%
  tabyl(parity, degree) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top') %>%
  kbl(caption = 'Ego Degree Centrality by Parity (pcq209 -- Missing Values set to 0)') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# calculate degree centrality by ego education
# 0, 1-8, 9+
ego_ego_met %>%
  select(deg, edu) %>%
  rename(education = edu, degree = deg) %>%
  mutate(education = case_when(education == 0 ~ 'None',
                         education > 0 & education <= 8 ~ '1-8',
                         education > 8 ~ '9+')) %>%
  mutate(education = ordered(education, levels = c('None', '1-8', '9+'))) %>%
  tabyl(education, degree) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top') %>%
  kbl(caption = 'Ego Degree Centrality by Education (pcq103)') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# calculate degree centrality by ego caste
# 0, 1-8, 9+
ego_ego_met %>%
  select(deg, caste) %>%
  rename(degree = deg) %>%
  mutate(caste = case_when(caste == 1 ~ 'Scheduled Caste',
                           caste == 2 ~ 'Scheduled Tribe',
                           caste == 3 ~ 'Other Backward Class',
                           caste == 4 ~ 'None of Them')) %>%
  mutate(caste = ordered(caste, levels = c('Scheduled Caste', 'Scheduled Tribe', 
                                       'Other Backward Class', 'None of Them'))) %>%
  tabyl(caste, degree) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top') %>%
  kbl(caption = 'Ego Degree Centrality by Caste (pcq111)') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# calculate degree centrality by ego employment
# worked ever, 1 = yes, 2 = no
ego_ego_met %>%
  select(deg, ever_worked) %>%
  rename(degree = deg) %>%
  tabyl(ever_worked, degree) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top') %>%
  kbl(caption = 'Ego Degree Centrality by Whether Ego has Ever Worked (pcq106)') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# worked in the last year, 1-3 = yes, 2 or NA = no
ego_ego_met %>%
  select(deg, worked_last_year) %>%
  rename(degree = deg) %>%
  mutate(worked_last_year = case_when(worked_last_year >= 1 & worked_last_year <= 3 ~ 'Yes',
                                      worked_last_year == 4 | is.na(worked_last_year)  ~ 'No')) %>%
  tabyl(worked_last_year, degree) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top') %>%
  kbl(caption = 'Ego Degree Centrality by Whether Ego has Worked in the Last Year (pcq107)') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# calculate degree centrality by ego's husband migrant
# yes = 3-7, no = 1-2
ego_ego_met %>%
  select(deg, husband_migrant) %>%
  rename(degree = deg) %>%
  mutate(husband_migrant = case_when(husband_migrant < 3 ~ 'No',
                                     husband_migrant >= 3 & husband_migrant <= 5 ~ 'Yes')) %>%
  tabyl(husband_migrant, degree) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top') %>%
  kbl(caption = "Ego Degree Centrality by Whether Ego's Husband is Migrant (pcq118)") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# ego table by block
ego_ego_met %>% 
            group_by(block) %>% 
            summarize(district = district[1],
                      geography = geography[1],
                      degree = mean(deg, na.rm = T) %>% round(2),
                      betweenness = mean(bet, na.rm = T) %>% round(2),
                      closeness = mean(clo, na.rm = T) %>% round(2)) %>%
            mutate(n = ego_ego_met %>% group_by(block) %>% tally() %>% .$n) %>%
  arrange(geography, block) %>%
  kbl(caption = 'Ego Mean Degree, Betweenness and Closeness Centrality by Block') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# write ego table by district
ego_ego_met %>% 
            group_by(district) %>% 
            summarize(geography = geography[1],
                      degree = mean(deg, na.rm = T) %>% round(2),
                      betweenness = mean(bet, na.rm = T) %>% round(2),
                      closeness = mean(clo, na.rm = T) %>% round(2)) %>%
            mutate(n = ego_ego_met %>% group_by(district) %>% tally() %>% .$n) %>%
  arrange(geography) %>%
  kbl(caption = 'Ego Mean Degree, Betweenness and Closeness Centrality by District') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# # write ego table by geography
# ego_ego_met %>% 
#             group_by(geography) %>% 
#             summarize(degree = mean(deg, na.rm = T) %>% round(2),
#                       betweenness = mean(bet, na.rm = T) %>% round(2),
#                       closeness = mean(clo, na.rm = T) %>% round(2)) %>%
#             mutate(n = ego_ego_met %>% group_by(district) %>% tally() %>% .$n) %>%
#   kbl(caption = 'Ego Mean Degree, Betweenness and Closeness Centrality by Geography') %>%
#   kable_classic_2('hover', full_width = F, position = 'left')
```
## B) Alters in Ego's Network

```{r, echo = F, warning = F, message = F, results = 'asis'}
# measures based on alter
# alter degree centrality
# alter betweenness centrality
ego_alt_met <- gr_list %>%
  map_dfr(~ tibble(mean_deg = mean(degree(.x)),
                   mean_bet = mean(betweenness(.x, weights = NA)),
                   deg_centr = centr_degree(.x)$centralization,
                   mean_clo = mean(closeness(.x, weights = NA)),
                   dens = edge_density(.x)),
          .id = 'ego_id')

# alter mean degree table
ego_alt_met %>% tabyl(mean_deg) %>% round(2) %>%
  rename(mean_degree = mean_deg) %>%
  kbl(caption = 'Alter Mean Degree Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# alter mean betweeness table
ego_alt_met %>% tabyl(mean_bet) %>% round(2) %>%
  rename(mean_betweenness = mean_bet) %>%
  kbl(caption = 'Alter Mean Betweenness Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# alter mean closeness table
ego_alt_met %>% tabyl(mean_clo) %>% round(2) %>%
  rename(mean_closeness = mean_clo) %>%
  kbl(caption = 'Alter Mean Closeness Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# write alter density table
ego_alt_met %>% tabyl(dens) %>% round(2) %>%
  rename(density = dens) %>%
  kbl(caption = 'Alter Density') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# sort ego_df and ego_alt_met by ego_id
ego_alt_met %<>% arrange(ego_id)
ego_df %<>% arrange(ego_id)

# make sure ego_ids match
# sum(ego_alt_met$ego_id == ego_df$ego_id)

# add district and block columns to ego_alt_met
ego_alt_met %<>% add_column(geography = ego_df$geography,
                            district = ego_df$district_name,
                            block = ego_df$block_name)

# write ego_alt table by block
ego_alt_met %>% 
            group_by(block) %>% 
            summarize(district = district[1],
                      geography = geography[1],
                      mean_degree = mean(mean_deg, na.rm = T) %>% round(2),
                      mean_betweenness = mean(mean_bet, na.rm = T) %>% round(2),
                      mean_closeness = mean(mean_clo, na.rm = T) %>% round(2),
                      mean_density = mean(dens, na.rm = T) %>% round(2)) %>%
            mutate(n = ego_alt_met %>% group_by(block) %>% tally() %>% .$n) %>%
  arrange(geography, block) %>%
  kbl(caption = 'Alter Mean Degree, Betweenness, Closeness Centrality, and Density by Block') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# write ego_alt table by district
ego_alt_met %>% 
            group_by(district) %>% 
            summarize(geography = geography[1],
                      mean_degree = mean(mean_deg, na.rm = T) %>% round(2),
                      mean_betweenness = mean(mean_bet, na.rm = T) %>% round(2),
                      mean_closeness = mean(mean_clo, na.rm = T) %>% round(2),
                      mean_density = mean(dens, na.rm = T) %>% round(2)) %>%
            mutate(n = ego_alt_met %>% group_by(district) %>% tally() %>% .$n) %>%
  arrange(geography) %>%
  kbl(caption = 'Alter Mean Degree, Betweenness, Closeness Centrality, and Density by District') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# # write ego_alt table by geography
# ego_alt_met %>% 
#             group_by(geography) %>% 
#             summarize(mean_degree = mean(mean_deg, na.rm = T) %>% round(2),
#                       mean_betweenness = mean(mean_bet, na.rm = T) %>% round(2),
#                       mean_closeness = mean(mean_clo, na.rm = T) %>% round(2),
#                       mean_density = mean(dens, na.rm = T) %>% round(2)) %>%
#             mutate(n = ego_alt_met %>% group_by(district) %>% tally() %>% .$n) %>%
#   kbl(caption = 'Alter Mean Degree, Betweenness, Closeness Centrality, and Density by Geography') %>%
#   kable_classic_2('hover', full_width = F, position = 'left')

```

## C) Alter Metrics (Alter Survey)

```{r, echo = F, warning = F, message = F, results = 'asis'}
########################################
### ALTER NETWORK DATA BASIC METRICS ###
########################################

# load alter igraph objects
load(alter_igraph_f)

# create table of unique blocks showing district as well
# write.csv(alter_df %>% select(district_name, block_name) %>% distinct(block_name, .keep_all = T), 
#          file = 'results/alter_district_block.csv', row.names = F)

# measures based on alter
# alter degree centrality
alt_alt_met <- gr_list_a_alt %>%
  map_dfr(~ tibble(deg = degree(.x, v = 'ego'),
                   bet = betweenness(.x, v = 'ego', weights = NA),
                   clo = closeness(.x, v = 'ego', weights = NA)),
          .id = 'alter_id')

# alter degree centrality table
alt_alt_met %>% tabyl(deg) %>% round(2) %>%
  rename(degree = deg) %>%
  kbl(caption = 'Alter Degree Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# alter betweeness centrality table
alt_alt_met %>% tabyl(bet) %>% round(2) %>%
  rename(betweenness = bet) %>%
  kbl(caption = 'Alter Betweenness Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# alter closeness table
alt_alt_met %>% tabyl(clo) %>% round(2) %>%
  rename(closeness = clo) %>%
  kbl(caption = 'Alter Closeness Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# sort alter_df and alt_alt_met by ego_id
alt_alt_met %<>% arrange(alter_id)
alter_df %<>% arrange(alter_id)

# make sure alter_ids match
# sum(alt_alt_met$alter_id == alter_df$alter_id)

# add district, block, age, education, caste columns to alt_alt_met
alt_alt_met %<>% add_column(geography = alter_df$geography,
                            district = alter_df$district_name,
                            block = alter_df$block_name,
                            age = alter_df$age,
                            edu = alter_df$education,
                            caste = alter_df$caste)

# write alt_alt table by block
alt_alt_met %>% 
            group_by(block) %>% 
            summarize(district = district[1],
                      geography = geography[1],
                      degree = mean(deg, na.rm = T) %>% round(2),
                      betweenness = mean(bet, na.rm = T) %>% round(2),
                      closeness = mean(clo, na.rm = T) %>% round(2)) %>%
            mutate(n = alt_alt_met %>% group_by(block) %>% tally() %>% .$n) %>%
  arrange(geography, district, block) %>%
  kbl(caption = 'Alter Mean Degree, Betweenness and Closeness Centrality by Block') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# write alt_alt table by district
alt_alt_met %>% 
            group_by(district) %>% 
            summarize(geography = geography[1],
                      degree = mean(deg, na.rm = T) %>% round(2),
                      betweenness = mean(bet, na.rm = T) %>% round(2),
                      closeness = mean(clo, na.rm = T) %>% round(2)) %>%
            mutate(n = alt_alt_met %>% group_by(district) %>% tally() %>% .$n) %>%
  arrange(geography, district) %>%
  kbl(caption = 'Alter Mean Degree, Betweenness and Closeness Centrality by District') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# write alt_alt table by geography
alt_alt_met %>% 
            group_by(geography) %>% 
            summarize(degree = mean(deg, na.rm = T) %>% round(2),
                      betweenness = mean(bet, na.rm = T) %>% round(2),
                      closeness = mean(clo, na.rm = T) %>% round(2)) %>%
            mutate(n = alt_alt_met %>% group_by(geography) %>% tally() %>% .$n) %>%
  kbl(caption = 'Alter Mean Degree, Betweenness and Closeness Centrality by Geography') %>%
  kable_classic_2('hover', full_width = F, position = 'left')
```

## D) Alter's Alters in Alter's Network (Alter Survey)

```{r, echo = F, warning = F, message = F, results = 'asis'}
# measures based on aalter
# aalter degree centrality
# aalter betweenness centrality
alt_aalt_met <- gr_list_a %>%
  map_dfr(~ tibble(mean_deg = mean(degree(.x)),
                   mean_bet = mean(betweenness(.x, weights = NA)),
                   deg_centr = centr_degree(.x)$centralization,
                   mean_clo = mean(closeness(.x, weights = NA)),
                   dens = edge_density(.x)),
          .id = 'alter_id')

# alter mean degree table
alt_aalt_met %>% tabyl(mean_deg) %>% round(2) %>% 
  rename(mean_degree = mean_deg) %>%
  kbl(caption = 'AAlter Mean Degree Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# alter mean betweeness table
alt_aalt_met %>% tabyl(mean_bet) %>% round(2) %>%
  rename(mean_betweenness = mean_bet) %>%
  kbl(caption = 'AAlter Mean Betweenness Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# alter mean closeness table
alt_aalt_met %>% tabyl(mean_clo) %>% round(2) %>%
  rename(mean_closeness = mean_clo) %>%
  kbl(caption = 'AAlter Mean Closeness Centrality') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# alter density table
alt_aalt_met %>% tabyl(dens) %>% round(2) %>%
  rename(density = dens) %>%
  kbl(caption = 'AAlter Density') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# sort alter_df and alt_aalt_met by ego_id
alt_aalt_met %<>% arrange(alter_id)
alter_df %<>% arrange(alter_id)

# make sure alter_ids match
# sum(alt_aalt_met$alter_id == alter_df$alter_id)

# add district and block columns to alt_aalt_met
alt_aalt_met %<>% add_column(geography = alter_df$geography,
                             district = alter_df$district_name,
                            block = alter_df$block_name)

# write alt_aalt table by block
alt_aalt_met %>% 
            group_by(block) %>% 
            summarize(district = district[1],
                      geography = geography[1],
                      mean_degree = mean(mean_deg, na.rm = T) %>% round(2),
                      mean_betweenness = mean(mean_bet, na.rm = T) %>% round(2),
                      mean_closeness = mean(mean_clo, na.rm = T) %>% round(2),
                      mean_density = mean(dens, na.rm = T) %>% round(2)) %>%
            mutate(n = alt_aalt_met %>% group_by(block) %>% tally() %>% .$n) %>%
  arrange(geography, district, block) %>%
  kbl(caption = 'AAlter Mean Degree, Betweenness, Closeness Centrality, and Density by Block') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# write alt_aalt table by district
alt_aalt_met %>% 
            group_by(district) %>% 
            summarize(geography = geography[1],
                      mean_degree = mean(mean_deg, na.rm = T) %>% round(2),
                      mean_betweenness = mean(mean_bet, na.rm = T) %>% round(2),
                      mean_closeness = mean(mean_clo, na.rm = T) %>% round(2),
                      mean_density = mean(dens, na.rm = T) %>% round(2)) %>%
            mutate(n = alt_aalt_met %>% group_by(district) %>% tally() %>% .$n) %>%
  arrange(geography, district) %>%
  kbl(caption = 'AAlter Mean Degree, Betweenness, Closeness Centrality, and Density by District') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# write alt_aalt table by geography
alt_aalt_met %>% 
            group_by(geography) %>% 
            summarize(mean_degree = mean(mean_deg, na.rm = T) %>% round(2),
                      mean_betweenness = mean(mean_bet, na.rm = T) %>% round(2),
                      mean_closeness = mean(mean_clo, na.rm = T) %>% round(2),
                      mean_density = mean(dens, na.rm = T) %>% round(2)) %>%
            mutate(n = alt_aalt_met %>% group_by(geography) %>% tally() %>% .$n) %>%
  kbl(caption = 'AAlter Mean Degree, Betweenness, Closeness Centrality, and Density by Geography') %>%
  kable_classic_2('hover', full_width = F, position = 'left')

```

## E) Figures

```{r, echo = F, warning = F, message = F, results = 'asis'}

############################################
### FIGURES OF DEGREE CENTRALITY OVERALL ###
############################################

# degree centrality of ego and alter
# first add ego
deg <- tibble(id = ego_ego_met$ego_id,
              deg = ego_ego_met$deg,
              district = ego_ego_met$district,
              age = ego_ego_met$age,
              edu = ego_ego_met$edu,
              caste = ego_ego_met$caste,
              group = 'ego') 

# second add alter
deg <- rbind(deg, tibble(id = alt_alt_met$alter_id,
                         deg = alt_alt_met$deg,
                         district = alt_alt_met$district,
                         age = alt_alt_met$age,
                         edu = alt_alt_met$edu,
                         caste = alt_alt_met$caste,
                         group = 'alter')) 

# change ego, edu, caste to numeric
deg %<>% mutate(age = as.numeric(age) %>% factor,
                edu = as.numeric(edu) %>% factor,
                caste = as.numeric(caste) %>% factor)

# reshape df
deg_sum <- deg %>% group_by(group) %>% count(deg)

# add missing val for ego
deg_sum <- rbind(deg_sum, tibble(group = 'ego',
                                 deg = 1,
                                 n = 0))

# generate colorscale
# colscale_egoalt <- scale_fill_manual(name = "Group", values = c('ego' = '#CCBB44', 'alter' = '#EE6677',
#                                                                 'Overall' = '#4477AA'))
colscale_egoalt <- scale_fill_manual(name = "Group", values = c('ego' = '#CCBB44', 'alter' = '#EE6677'),
                                     labels = c('ego' = 'Ego', 'alter' = 'Alter'))

# # plot degree by n
# ggplot(deg_sum, aes(x = deg %>% as.factor, y = n, fill = ordered(group, levels = c('ego', 'alter')))) +
#   geom_bar(stat = 'identity',
#            position = position_dodge()) +
#   theme_bw() +
#   labs(x = 'Degree', y = 'N', fill = 'Group') +
#   colscale_egoalt +  xlim('0', '1', '2', '3', '4', '5') +
#   ggtitle('Degree Centrality of Ego and Alter') +
#   theme(text = element_text(size=20))

# ggsave('results/figures/deg_cent_ego_alt_plot_n.png')

# plot degree by perc
deg_sum$perc <- NA
deg_sum$perc[deg_sum$group == 'alter'] <- deg_sum$n[deg_sum$group == 'alter']/sum(deg_sum$n[deg_sum$group == 'alter'])
deg_sum$perc[deg_sum$group == 'ego'] <- deg_sum$n[deg_sum$group == 'ego']/sum(deg_sum$n[deg_sum$group == 'ego'])
deg_sum$perc <- round(deg_sum$perc, 2)

ggplot(deg_sum, aes(x = deg %>% as.factor, y = perc*100, fill = ordered(group, levels = c('ego', 'alter')))) +
  geom_bar(stat = 'identity',
           position = position_dodge()) +
  theme_bw() +
  labs(x = 'Degree', y = 'Percent by Group', fill = 'Group') +
  colscale_egoalt +  xlim('0', '1', '2', '3', '4', '5') +
  ggtitle('Degree Centrality of Ego and Alter') +
  theme(text = element_text(size=20))

# ggsave('results/figures/deg_cent_ego_alt_plot_perc.png')

########################################
### FIGURES OF DEG CENTRALITY BY AGE ###
########################################

# segment df by ego age
deg_ego_age <- deg %>% 
  filter(group == 'ego') %>% 
  group_by(age) %>% 
  count(deg)

# add in missing values
for(i in unique(deg_ego_age$age)){
  for(j in 0:5){
    check <- deg_ego_age %>%
      filter(age == i,
             deg == j)
    if(NROW(check) == 0){
      deg_ego_age %<>% rbind(tibble(age = i,
                                    deg = j,
                                    n = 0))
    }
  }
}

# generate colorscale
colscale_egoage <- scale_fill_manual(name = "Age", values = c('18' = '#4477AA', '19' = '#66CCEE',
                                                              '20' = '#228833', '21' = '#CCBB44',
                                                              '22' = '#EE6677', '23' = '#AA3377',
                                                              '24' = '#BBBBBB'))

# # plot degree by ego age
# ggplot(deg_ego_age, aes(x = deg %>% as.factor, y = n, fill = age)) +
#   geom_bar(stat = 'identity',
#            position = position_dodge()) +
#   theme_bw() +
#   colscale_egoage +
#   labs(x = 'Degree', y = 'N', fill = 'Age') +  
#   xlim('0', '1', '2', '3', '4', '5') +
#   ggtitle('Degree Centrality of Ego by Age') +
#   theme(text = element_text(size=20))
# 
# ggsave('results/figures/deg_cent_ego_age_plot_n.png')

# plot degree by perc
deg_ego_age$perc <- NA
for(i in unique(deg_ego_age$age)){
  deg_ego_age$perc[deg_ego_age$age == i] <- deg_ego_age$n[deg_ego_age$age == i]/sum(deg_ego_age$n[deg_ego_age$age == i])
}
deg_ego_age$perc <- round(deg_ego_age$perc, 2)

ggplot(deg_ego_age, aes(x = deg %>% as.factor, y = perc*100, fill = age)) +
  geom_bar(stat = 'identity',
           position = position_dodge()) +
  theme_bw() +
  colscale_egoage + 
  labs(x = 'Degree', y = 'Percent by Age Group', fill = 'Age') +  
  xlim('0', '1', '2', '3', '4', '5') +
  ggtitle('Degree Centrality of Ego by Age') +
  theme(text = element_text(size=20))

# ggsave('results/figures/deg_cent_ego_age_plot_perc.png')

# segment df by alter age
deg_alt_age <- deg %>% 
  filter(group == 'alter')

# factor age groups
deg_alt_age %<>% mutate(age = age %>%
                          as.character %>%
                          as.numeric %>%
                          cut(c(17,19,29,39,49,59,101),
                              labels = c('18-19', '20-29', '30-39', '40-49', '50-59','60+'))) %>%
  group_by(age) %>% 
  count(deg)

# add in missing values
for(i in unique(deg_alt_age$age)){
  for(j in 0:5){
    check <- deg_alt_age %>%
      filter(age == i,
             deg == j)
    if(NROW(check) == 0){
      deg_alt_age %<>% rbind(tibble(age = i,
                                    deg = j,
                                    n = 0))
    }
  }
}

# generate colorscale
colscale_altage <- scale_fill_manual(name = "Age", values = c('18-19' = '#4477AA', '20-29' = '#66CCEE',
                                                              '30-39' = '#228833', '40-49' = '#CCBB44',
                                                              '50-59' = '#EE6677', '60+' = '#AA3377'))

# # plot degree by alter age
# ggplot(deg_alt_age, aes(x = deg %>% as.factor, y = n, fill = age)) +
#   geom_bar(stat = 'identity',
#            position = position_dodge()) +
#   theme_bw() +
#   colscale_altage +
#   labs(x = 'Degree', y = 'N', fill = 'Age') +  
#   xlim('0', '1', '2', '3', '4', '5') +
#   ggtitle('Degree Centrality of Alter by Age') +
#   theme(text = element_text(size=20))
# 
# ggsave('results/figures/deg_cent_alt_age_plot_n.png')

# plot degree by perc
deg_alt_age$perc <- NA
for(i in unique(deg_alt_age$age)){
  deg_alt_age$perc[deg_alt_age$age == i] <- deg_alt_age$n[deg_alt_age$age == i]/sum(deg_alt_age$n[deg_alt_age$age == i])
}
deg_alt_age$perc <- round(deg_alt_age$perc, 2)

ggplot(deg_alt_age, aes(x = deg %>% as.factor, y = perc*100, fill = age)) +
  geom_bar(stat = 'identity',
           position = position_dodge()) +
  theme_bw() +
  colscale_altage + 
  labs(x = 'Degree', y = 'Percent by Age Group', fill = 'Age') +  
  xlim('0', '1', '2', '3', '4', '5') +
  ggtitle('Degree Centrality of Alter by Age') +
  theme(text = element_text(size=20))

# ggsave('results/figures/deg_cent_alt_age_plot_perc.png')

##########################################
### FIGURES OF DEG CENTRALITY BY CASTE ###
##########################################

# segment df by ego caste
deg_ego_caste <- deg %>% 
  filter(group == 'ego')

# factor caste groups
deg_ego_caste %<>% mutate(caste = caste %>%
                          as.character %>%
                          as.numeric %>%
                          cut(c(0,2,3,4),
                              labels = c('Schedule Caste/Tribe', 'Other Backward Class', 'Other'))) %>%
  group_by(caste) %>% 
  count(deg)

# add in missing values
for(i in unique(deg_ego_caste$caste)){
  for(j in 0:5){
    check <- deg_ego_caste %>%
      filter(caste == i,
             deg == j)
    if(NROW(check) == 0){
      deg_ego_caste %<>% rbind(tibble(caste = i,
                                    deg = j,
                                    n = 0))
    }
  }
}

# generate colorscale
colscale_caste <- scale_fill_manual(name = "Caste", values = c('Schedule Caste/Tribe' = '#4477AA',
                                                              'Other Backward Class' = '#228833', 
                                                              'Other' = '#EE6677'))

# # plot degree by ego caste
# ggplot(deg_ego_caste, aes(x = deg %>% as.factor, 
#                           y = n, 
#                           fill = ordered(caste,
#                                          levels = c('Schedule Caste/Tribe',
#                                                     'Other Backward Class',
#                                                     'Other')))) +
#   geom_bar(stat = 'identity',
#            position = position_dodge()) +
#   theme_bw() +
#   colscale_caste +
#   labs(x = 'Degree', y = 'N', fill = 'Caste') +  
#   xlim('0', '1', '2', '3', '4', '5') +
#   ggtitle('Degree Centrality of Ego by Caste') +
#   theme(text = element_text(size=20))
# 
# ggsave('results/figures/deg_cent_ego_caste_plot_n.png')

# plot degree by perc
deg_ego_caste$perc <- NA
for(i in unique(deg_ego_caste$caste)){
  deg_ego_caste$perc[deg_ego_caste$caste == i] <- deg_ego_caste$n[deg_ego_caste$caste == i]/sum(deg_ego_caste$n[deg_ego_caste$caste == i])
}
deg_ego_caste$perc <- round(deg_ego_caste$perc, 2)

ggplot(deg_ego_caste, aes(x = deg %>% as.factor,
                          y = perc*100, 
                          fill = ordered(caste, 
                                         levels = c('Schedule Caste/Tribe', 
                                                   'Other Backward Class', 
                                                   'Other')))) +                                 
  geom_bar(stat = 'identity',
           position = position_dodge()) +
  theme_bw() +
  colscale_caste + 
  labs(x = 'Degree', y = 'Percent by Caste Group', fill = 'Caste') +  
  xlim('0', '1', '2', '3', '4', '5') +
  ggtitle('Degree Centrality of Ego by Caste') +
  theme(text = element_text(size=20))

# ggsave('results/figures/deg_cent_ego_caste_plot_perc.png')

# segment df by alter caste
deg_alt_caste <- deg %>% 
  filter(group == 'alter')

# factor caste groups
deg_alt_caste %<>% mutate(caste = caste %>%
                            as.character %>%
                            as.numeric %>%
                            cut(c(0,2,3,4),
                                labels = c('Schedule Caste/Tribe', 'Other Backward Class', 'Other'))) %>%
  group_by(caste) %>% 
  count(deg)

# add in missing values
for(i in unique(deg_alt_caste$caste)){
  for(j in 0:5){
    check <- deg_alt_caste %>%
      filter(caste == i,
             deg == j)
    if(NROW(check) == 0){
      deg_alt_caste %<>% rbind(tibble(caste = i,
                                      deg = j,
                                      n = 0))
    }
  }
}

# # plot degree by alter caste
# ggplot(deg_alt_caste, aes(x = deg %>% as.factor, 
#                           y = n, 
#                           fill = ordered(caste,
#                                          levels = c('Schedule Caste/Tribe',
#                                                     'Other Backward Class',
#                                                     'Other')))) +
#   geom_bar(stat = 'identity',
#            position = position_dodge()) +
#   theme_bw() +
#   colscale_caste +
#   labs(x = 'Degree', y = 'N', fill = 'Caste') +  
#   xlim('0', '1', '2', '3', '4', '5') +
#   ggtitle('Degree Centrality of Alter by Caste') +
#   theme(text = element_text(size=20))
# 
# ggsave('results/figures/deg_cent_alt_caste_plot_n.png')

# plot degree by perc
deg_alt_caste$perc <- NA
for(i in unique(deg_alt_caste$caste)){
  deg_alt_caste$perc[deg_alt_caste$caste == i] <- deg_alt_caste$n[deg_alt_caste$caste == i]/sum(deg_alt_caste$n[deg_alt_caste$caste == i])
}
deg_alt_caste$perc <- round(deg_alt_caste$perc, 2)

ggplot(deg_alt_caste, aes(x = deg %>% as.factor,
                          y = perc*100, 
                          fill = ordered(caste, 
                                         levels = c('Schedule Caste/Tribe', 
                                                    'Other Backward Class', 
                                                    'Other')))) +                                 
  geom_bar(stat = 'identity',
           position = position_dodge()) +
  theme_bw() +
  colscale_caste + 
  labs(x = 'Degree', y = 'Percent by Caste Group', fill = 'Caste') +  
  xlim('0', '1', '2', '3', '4', '5') +
  ggtitle('Degree Centrality of Alter by Caste') +
  theme(text = element_text(size=20))

# ggsave('results/figures/deg_cent_alt_caste_plot_perc.png')

##############################################
### FIGURES OF DEG CENTRALITY BY EDUCATION ###
##############################################

# segment df by ego education
deg_ego_edu <- deg %>% 
  filter(group == 'ego')

# factor caste groups
deg_ego_edu %<>% mutate(edu = edu %>%
                            as.character %>%
                            as.numeric %>%
                            cut(c(-1,0,8,100),
                                labels = c('None', '1-8', '9+'))) %>%
  group_by(edu) %>% 
  count(deg)

# add in missing values
for(i in unique(deg_ego_edu$edu)){
  for(j in 0:5){
    check <- deg_ego_edu %>%
      filter(edu == i,
             deg == j)
    if(NROW(check) == 0){
      deg_ego_edu %<>% rbind(tibble(edu = i,
                                      deg = j,
                                      n = 0))
    }
  }
}

# generate colorscale
colscale_edu <- scale_fill_manual(name = "Education", values = c('None' = '#4477AA',
                                                               '1-8' = '#228833', 
                                                               '9+' = '#EE6677'))

# # plot degree by ego education
# ggplot(deg_ego_edu, aes(x = deg %>% as.factor, 
#                           y = n, 
#                           fill = ordered(edu,
#                                          levels = c('None',
#                                                     '1-8',
#                                                     '9+')))) +
#   geom_bar(stat = 'identity',
#            position = position_dodge()) +
#   theme_bw() +
#   colscale_edu +
#   labs(x = 'Degree', y = 'N', fill = 'Education') +  
#   xlim('0', '1', '2', '3', '4', '5') +
#   ggtitle('Degree Centrality of Ego by Education') +
#   theme(text = element_text(size=20))
# 
# ggsave('results/figures/deg_cent_ego_edu_plot_n.png')

# plot degree by perc
deg_ego_edu$perc <- NA
for(i in unique(deg_ego_edu$edu)){
  deg_ego_edu$perc[deg_ego_edu$edu == i] <- deg_ego_edu$n[deg_ego_edu$edu == i]/sum(deg_ego_edu$n[deg_ego_edu$edu == i])
}
deg_ego_edu$perc <- round(deg_ego_edu$perc, 2)

ggplot(deg_ego_edu, aes(x = deg %>% as.factor,
                          y = perc*100, 
                          fill = ordered(edu,
                                          levels = c('None',
                                                     '1-8',
                                                     '9+')))) +                                 
  geom_bar(stat = 'identity',
           position = position_dodge()) +
  theme_bw() +
  colscale_edu + 
  labs(x = 'Degree', y = 'Percent by Education Group', fill = 'Education') +  
  xlim('0', '1', '2', '3', '4', '5') +
  ggtitle('Degree Centrality of Ego by Education') +
  theme(text = element_text(size=20))

# ggsave('results/figures/deg_cent_ego_edu_plot_perc.png')

# segment df by alter education
deg_alt_edu <- deg %>% 
  filter(group == 'alter')

# factor caste groups
deg_alt_edu %<>% mutate(edu = edu %>%
                          as.character %>%
                          as.numeric %>%
                          cut(c(-1,0,8,100),
                              labels = c('None', '1-8', '9+'))) %>%
  group_by(edu) %>% 
  count(deg)

# add in missing values
for(i in unique(deg_alt_edu$edu)){
  for(j in 0:5){
    check <- deg_alt_edu %>%
      filter(edu == i,
             deg == j)
    if(NROW(check) == 0){
      deg_alt_edu %<>% rbind(tibble(edu = i,
                                    deg = j,
                                    n = 0))
    }
  }
}

# # plot degree by ego education
# ggplot(deg_alt_edu, aes(x = deg %>% as.factor, 
#                         y = n, 
#                         fill = ordered(edu,
#                                        levels = c('None',
#                                                   '1-8',
#                                                   '9+')))) +
#   geom_bar(stat = 'identity',
#            position = position_dodge()) +
#   theme_bw() +
#   colscale_edu +
#   labs(x = 'Degree', y = 'N', fill = 'Education') +  
#   xlim('0', '1', '2', '3', '4', '5') +
#   ggtitle('Degree Centrality of Alter by Education') +
#   theme(text = element_text(size=20))
# 
# ggsave('results/figures/deg_cent_alt_edu_plot_n.png')

# plot degree by perc
deg_alt_edu$perc <- NA
for(i in unique(deg_alt_edu$edu)){
  deg_alt_edu$perc[deg_alt_edu$edu == i] <- deg_alt_edu$n[deg_alt_edu$edu == i]/sum(deg_alt_edu$n[deg_alt_edu$edu == i])
}
deg_alt_edu$perc <- round(deg_alt_edu$perc, 2)

ggplot(deg_alt_edu, aes(x = deg %>% as.factor,
                        y = perc*100, 
                        fill = ordered(edu,
                                       levels = c('None',
                                                  '1-8',
                                                  '9+')))) +                                 
  geom_bar(stat = 'identity',
           position = position_dodge()) +
  theme_bw() +
  colscale_edu + 
  labs(x = 'Degree', y = 'Percent by Education Group', fill = 'Education') +  
  xlim('0', '1', '2', '3', '4', '5') +
  ggtitle('Degree Centrality of Alter by Education') +
  theme(text = element_text(size=20))

# ggsave('results/figures/deg_cent_alt_edu_plot_perc.png')

```

```{r, echo = F, warning = F, message = F, results = 'asis', fig.width = 13,fig.height = 8}
##################################
### PLOTS OF NETWORK STRUCTURE ###
##################################

# density of 1st net
# ego_alt_met$dens[1]

# basic plot
ggraph(gr_list_ego[[1]], 'dh') +
  geom_edge_link(aes(linetype = as.factor(weight))) +
  geom_node_label(aes(label = name)) + 
  theme_graph(base_family = 'Helvetica') +
  scale_edge_linetype_manual(values = c('dotted', 'solid')) + 
  theme(legend.position="none") +
  ggtitle('Ego-Alter Network (Density = 1)')

# ggsave(filename = 'results/figures/ego_net_1.png')

# density of 1st net
# ego_alt_met$dens[108]

# basic plot2
ggraph(gr_list_ego[[108]], 'dh') +
  geom_edge_link(aes(linetype = as.factor(weight))) +
  geom_node_label(aes(label = name)) + 
  theme_graph(base_family = 'Helvetica') +
  scale_edge_linetype_manual(values = c('dotted', 'solid')) + 
  theme(legend.position="none") +
  ggtitle('Ego-Alter Network (Density = 0.7)')

# ggsave(filename = 'results/figures/ego_net_109.png')

# density of 1st net
# ego_alt_met$dens[80]

# basic plot2
ggraph(gr_list_ego[[80]], 'dh') +
  geom_edge_link(aes(linetype = as.factor(weight))) +
  geom_node_label(aes(label = name)) + 
  theme_graph(base_family = 'Helvetica') +
  scale_edge_linetype_manual(values = c('dotted', 'solid')) + 
  theme(legend.position="none") +
  ggtitle('Ego-Alter Network (Density = 0.6)')

# ggsave(filename = 'results/figures/ego_net_81.png')

```

```{r, echo = F, warning = F, message = F, results = 'asis'}

###########################################################
### CALCULATE HOMOPHILY AND HETEROGENEITY EGO AND ALTER ###
###########################################################

# this code loads csv data of ego and alter interviews
# and calculates homophily and homogeneity metrics

# load packages
library(magrittr)
library(egor)
library(janitor)
library(tidyverse)
library(readxl)
library(igraph)
library(readstata13)

#########################################
### LOAD EGO AND ALTER DATA AND CLEAN ###
#########################################

# load ego and alter cleaned data
ego <- read_excel(path = ego_data_f)

alter <-read_excel(path = alter_data_f)

# load pc data
ego_pc <- read_excel(path = ego_pc_f)

# load list of duplicate ids
dup_id <- read_excel(path = dup_id_f)

# remove first row with 'qe' names
ego <- ego[-1,]
alter <- alter[-1,]

# clean column names only keep part after last "."
ego_names <- sapply(colnames(ego), FUN = function(x){
  st <- str_split(x, pattern = glob2rx("*-*"))
  st <- st[[1]][length(st[[1]])]
  return(st)
})

names(ego_names) <- NULL
colnames(ego) <- ego_names

alter_names <- sapply(colnames(alter), FUN = function(x){
  st <- str_split(x, pattern = glob2rx("*-*"))
  st <- st[[1]][length(st[[1]])]
  return(st)
})

names(alter_names) <- NULL
colnames(alter) <- alter_names

rm(ego_names, alter_names)

# remove empty columns from "notes"
ego <- ego[,str_detect(colnames(ego), 'note') == F]
alter <- alter[,str_detect(colnames(alter), 'note') == F]

# replace character NA values with NA
ego[ego == "NA"] <- NA
alter[alter == "NA"] <- NA

# fix district, block and village in alter data
alter$district_name <- alter$`district name_clean`
alter$block_name <- alter$`block name_clean`
alter$village_name <- alter$`village name_clean`

# remove "clean" columns
alter <- alter %>% select(-c(`district name_clean`, `block name_clean`, `village name_clean`))

# add alter-alter tie columns to ego dataset so we can build edgelist below
# let's first extract the correct question so easier to look at
alter_know <- ego[,str_detect(colnames(ego), glob2rx('alter?_know?'))]

# set to numeric
alter_know <- sapply(alter_know, as.numeric)

# set "don't know" to 0 since then tie won't exist. both responses labeled 2 and 9
alter_know[alter_know == 2] <- 0
alter_know[alter_know == 9] <- 0

# create new df with only a single column for combinations
alter_know %<>% as.data.frame %>% 
  mutate(know12 = alter1_know2 + alter2_know1,
         know13 = alter1_know3 + alter3_know1,
         know14 = alter1_know4 + alter4_know1,
         know15 = alter1_know5 + alter5_know1,
         know23 = alter2_know3 + alter3_know2,
         know24 = alter2_know4 + alter4_know2,
         know25 = alter2_know5 + alter5_know2,
         know34 = alter3_know4 + alter4_know3,
         know35 = alter3_know5 + alter5_know3,
         know45 = alter4_know5 + alter5_know4)

# now set 0 to NA since we just want to identify tie or not
alter_know %<>% select(know12:know45)
alter_know[alter_know == 0] <- NA

# add simple know columns back into ego df
ego %<>% add_column(alter_know)
rm(alter_know)

# add aalter-aalter tie columns to alter dataset so we can build edgelist below
# let's first extract the correct question so easier to look at
alter_know <- alter[,str_detect(colnames(alter), glob2rx('alter?_know?'))]

# set to numeric
alter_know <- sapply(alter_know, as.numeric)

# set "don't know" to 0 since then tie won't exist. both responses labeled 2 and 9
alter_know[alter_know == 2] <- 0
alter_know[alter_know == 9] <- 0

# create new df with only a single column for combinations
alter_know %<>% as.data.frame %>% 
  mutate(know12 = alter1_know2 + alter2_know1,
         know13 = alter1_know3 + alter3_know1,
         know14 = alter1_know4 + alter4_know1,
         know15 = alter1_know5 + alter5_know1,
         know23 = alter2_know3 + alter3_know2,
         know24 = alter2_know4 + alter4_know2,
         know25 = alter2_know5 + alter5_know2,
         know34 = alter3_know4 + alter4_know3,
         know35 = alter3_know5 + alter5_know3,
         know45 = alter4_know5 + alter5_know4)

# now set 0 to NA since we just want to identify tie or not
alter_know %<>% select(know12:know45)
alter_know[alter_know == 0] <- NA

# add simple know columns back into alter df
alter %<>% add_column(alter_know)
rm(alter_know)

#####################
### HOMOPHILY EGO ###
#####################

# gender
# education
# number of family members
# number of non-family members close to
# practicing FP
# network composition: family/non-family (?)

# sort ego data and PC data by woman ID so can merge
ego %<>% arrange(woman_id)
ego_pc %<>% arrange(qe6) # qe6 is woman_id

# make sure ego_ids match
# sum(ego_pc$qe6 == ego$woman_id)

# build tibble of ego and alter attributes
ea <- rbind(tibble(ego_id = ego$woman_id,
                   alter_name = ego$alter1,
                   ego_sex = 2,
                   alt_sex = ego$alter1_sex,
                   ego_caste = ego_pc$pcq111,
                   alt_caste = ego$alter1_caste,
                   ego_edu = ego_pc$pcq103,
                   alt_edu = NA,
                   ego_fam = ego$family_members,
                   alt_fam = ego$alter1_family,
                   ego_friends = ego$friends,
                   alt_friends = ego$alter1_friends,
                   ego_neigh = ego$neighbours,
                   alt_neigh = ego$alter1_neighbours,
                   ego_using_fp = ego_pc$pcq312,
                   alt_using_fp = ego$alter1_using_fp,
                   ego_know_asha = ego$know_asha,
                   ego_know_anm = ego$know_anm,
                   ego_know_aww = ego$know_aww,
                   ego_know_shg = ego$know_shg,
                   ego_know_pra = ego$know_pradhan,
                   ego_know_pha = ego$know_pharmacist,
                   ego_know_doc = ego$know_doctor,
                   ego_know_rel = ego$know_religious_leader,
                   alt_know_asha = ego$alter1_asha,
                   alt_know_anm = ego$alter1_anm,
                   alt_know_aww = ego$alter1_aww,
                   alt_know_shg = ego$alter1_shg,
                   alt_know_pra = ego$alter1_pradhan,
                   alt_know_pha = ego$alter1_pharmacist,
                   alt_know_doc = ego$alter1_doctor,
                   alt_know_rel = ego$alter1_religious_leader,
                   ego_sons = ego_pc$pcq205s,
                   ego_daughters = ego_pc$pcq205d,
                   alt_sons = ego$alter1_sons,
                   alt_daughters = ego$alter1_daughters,
                   alt_residence = ego$alter1_residence,
                   alt_relationship = ego$alter1r,
                   alt_learned = ego$alter1_learned,
                   alt_encourage_fp = ego$alter1_encourage_fp,
                   alt_discuss_fp = ego$alter1_discuss_fp,
                   alt_help_ego = ego$alter1_help,
                   alt_helped_by_ego = ego$alter1_helped,
                   alt_against_advice = ego$alter1_follow_advice,
                   alt_support_no_child = ego$alter1_nochild),
            tibble(ego_id = ego$woman_id,
                   alter_name = ego$alter2,
                   ego_sex = 2,
                   alt_sex = ego$alter2_sex,
                   ego_caste = ego_pc$pcq111,
                   alt_caste = ego$alter2_caste,
                   ego_edu = ego_pc$pcq103,
                   alt_edu = NA,
                   ego_fam = ego$family_members,
                   alt_fam = ego$alter2_family,
                   ego_friends = ego$friends,
                   alt_friends = ego$alter2_friends,
                   ego_neigh = ego$neighbours,
                   alt_neigh = ego$alter2_neighbours,
                   ego_using_fp = ego_pc$pcq312,
                   alt_using_fp = ego$alter2_using_fp,
                   ego_know_asha = ego$know_asha,
                   ego_know_anm = ego$know_anm,
                   ego_know_aww = ego$know_aww,
                   ego_know_shg = ego$know_shg,
                   ego_know_pra = ego$know_pradhan,
                   ego_know_pha = ego$know_pharmacist,
                   ego_know_doc = ego$know_doctor,
                   ego_know_rel = ego$know_religious_leader,
                   alt_know_asha = ego$alter2_asha,
                   alt_know_anm = ego$alter2_anm,
                   alt_know_aww = ego$alter2_aww,
                   alt_know_shg = ego$alter2_shg,
                   alt_know_pra = ego$alter2_pradhan,
                   alt_know_pha = ego$alter2_pharmacist,
                   alt_know_doc = ego$alter2_doctor,
                   alt_know_rel = ego$alter2_religious_leader,
                   ego_sons = ego_pc$pcq205s,
                   ego_daughters = ego_pc$pcq205d,
                   alt_sons = ego$alter2_sons,
                   alt_daughters = ego$alter2_daughters,
                   alt_residence = ego$alter2_residence,
                   alt_relationship = ego$alter2r,
                   alt_learned = ego$alter2_learned,
                   alt_encourage_fp = ego$alter2_encourage_fp,
                   alt_discuss_fp = ego$alter2_discuss_fp,
                   alt_help_ego = ego$alter2_help,
                   alt_helped_by_ego = ego$alter2_helped,
                   alt_against_advice = ego$alter2_follow_advice,
                   alt_support_no_child = ego$alter2_nochild),
            tibble(ego_id = ego$woman_id,
                   alter_name = ego$alter3,
                   ego_sex = 2,
                   alt_sex = ego$alter3_sex,
                   ego_caste = ego_pc$pcq111,
                   alt_caste = ego$alter3_caste,
                   ego_edu = ego_pc$pcq103,
                   alt_edu = NA,
                   ego_fam = ego$family_members,
                   alt_fam = ego$alter3_family,
                   ego_friends = ego$friends,
                   alt_friends = ego$alter3_friends,
                   ego_neigh = ego$neighbours,
                   alt_neigh = ego$alter3_neighbours,
                   ego_using_fp = ego_pc$pcq312,
                   alt_using_fp = ego$alter3_using_fp,
                   ego_know_asha = ego$know_asha,
                   ego_know_anm = ego$know_anm,
                   ego_know_aww = ego$know_aww,
                   ego_know_shg = ego$know_shg,
                   ego_know_pra = ego$know_pradhan,
                   ego_know_pha = ego$know_pharmacist,
                   ego_know_doc = ego$know_doctor,
                   ego_know_rel = ego$know_religious_leader,
                   alt_know_asha = ego$alter3_asha,
                   alt_know_anm = ego$alter3_anm,
                   alt_know_aww = ego$alter3_aww,
                   alt_know_shg = ego$alter3_shg,
                   alt_know_pra = ego$alter3_pradhan,
                   alt_know_pha = ego$alter3_pharmacist,
                   alt_know_doc = ego$alter3_doctor,
                   alt_know_rel = ego$alter3_religious_leader,
                   ego_sons = ego_pc$pcq205s,
                   ego_daughters = ego_pc$pcq205d,
                   alt_sons = ego$alter3_sons,
                   alt_daughters = ego$alter3_daughters,
                   alt_residence = ego$alter3_residence,
                   alt_relationship = ego$alter3r,
                   alt_learned = ego$alter3_learned,
                   alt_encourage_fp = ego$alter3_encourage_fp,
                   alt_discuss_fp = ego$alter3_discuss_fp,
                   alt_help_ego = ego$alter3_help,
                   alt_helped_by_ego = ego$alter3_helped,
                   alt_against_advice = ego$alter3_follow_advice,
                   alt_support_no_child = ego$alter3_nochild),
            tibble(ego_id = ego$woman_id,
                   alter_name = ego$alter4,
                   ego_sex = 2,
                   alt_sex = ego$alter4_sex,
                   ego_caste = ego_pc$pcq111,
                   alt_caste = ego$alter4_caste,
                   ego_edu = ego_pc$pcq103,
                   alt_edu = NA,
                   ego_fam = ego$family_members,
                   alt_fam = ego$alter4_family,
                   ego_friends = ego$friends,
                   alt_friends = ego$alter4_friends,
                   ego_neigh = ego$neighbours,
                   alt_neigh = ego$alter4_neighbours,
                   ego_using_fp = ego_pc$pcq312,
                   alt_using_fp = ego$alter4_using_fp,
                   ego_know_asha = ego$know_asha,
                   ego_know_anm = ego$know_anm,
                   ego_know_aww = ego$know_aww,
                   ego_know_shg = ego$know_shg,
                   ego_know_pra = ego$know_pradhan,
                   ego_know_pha = ego$know_pharmacist,
                   ego_know_doc = ego$know_doctor,
                   ego_know_rel = ego$know_religious_leader,
                   alt_know_asha = ego$alter4_asha,
                   alt_know_anm = ego$alter4_anm,
                   alt_know_aww = ego$alter4_aww,
                   alt_know_shg = ego$alter4_shg,
                   alt_know_pra = ego$alter4_pradhan,
                   alt_know_pha = ego$alter4_pharmacist,
                   alt_know_doc = ego$alter4_doctor,
                   alt_know_rel = ego$alter4_religious_leader,
                   ego_sons = ego_pc$pcq205s,
                   ego_daughters = ego_pc$pcq205d,
                   alt_sons = ego$alter4_sons,
                   alt_daughters = ego$alter4_daughters,
                   alt_residence = ego$alter4_residence,
                   alt_relationship = ego$alter4r,
                   alt_learned = ego$alter4_learned,
                   alt_encourage_fp = ego$alter4_encourage_fp,
                   alt_discuss_fp = ego$alter4_discuss_fp,
                   alt_help_ego = ego$alter4_help,
                   alt_helped_by_ego = ego$alter4_helped,
                   alt_against_advice = ego$alter4_follow_advice,
                   alt_support_no_child = ego$alter4_nochild),
            tibble(ego_id = ego$woman_id,
                   alter_name = ego$alter5,
                   ego_sex = 2,
                   alt_sex = ego$alter5_sex,
                   ego_caste = ego_pc$pcq111,
                   alt_caste = ego$alter5_caste,
                   ego_edu = ego_pc$pcq103,
                   alt_edu = NA,
                   ego_fam = ego$family_members,
                   alt_fam = ego$alter5_family,
                   ego_friends = ego$friends,
                   alt_friends = ego$alter5_friends,
                   ego_neigh = ego$neighbours,
                   alt_neigh = ego$alter5_neighbours,
                   ego_using_fp = ego_pc$pcq312,
                   alt_using_fp = ego$alter5_using_fp,
                   ego_know_asha = ego$know_asha,
                   ego_know_anm = ego$know_anm,
                   ego_know_aww = ego$know_aww,
                   ego_know_shg = ego$know_shg,
                   ego_know_pra = ego$know_pradhan,
                   ego_know_pha = ego$know_pharmacist,
                   ego_know_doc = ego$know_doctor,
                   ego_know_rel = ego$know_religious_leader,
                   alt_know_asha = ego$alter5_asha,
                   alt_know_anm = ego$alter5_anm,
                   alt_know_aww = ego$alter5_aww,
                   alt_know_shg = ego$alter5_shg,
                   alt_know_pra = ego$alter5_pradhan,
                   alt_know_pha = ego$alter5_pharmacist,
                   alt_know_doc = ego$alter5_doctor,
                   alt_know_rel = ego$alter5_religious_leader,
                   ego_sons = ego_pc$pcq205s,
                   ego_daughters = ego_pc$pcq205d,
                   alt_sons = ego$alter5_sons,
                   alt_daughters = ego$alter5_daughters,
                   alt_residence = ego$alter5_residence,
                   alt_relationship = ego$alter5r,
                   alt_learned = ego$alter5_learned,
                   alt_encourage_fp = ego$alter5_encourage_fp,
                   alt_discuss_fp = ego$alter5_discuss_fp,
                   alt_help_ego = ego$alter5_help,
                   alt_helped_by_ego = ego$alter5_helped,
                   alt_against_advice = ego$alter5_follow_advice,
                   alt_support_no_child = ego$alter5_nochild))

# drop rows for missing alters
ea %<>% filter(is.na(alter_name) == F)

##############
### GENDER ###
##############

# check unique values
# unique(ea$ego_sex)
# unique(ea$alt_sex)

# set to numeric
ea$alt_sex <- as.numeric(ea$alt_sex)

# summarise
sex <- ea$ego_sex == ea$alt_sex
dat <- tabyl(sex) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# create homophily output
homo <- tibble(metric = 'Gender (%)',
               value = dat %>% filter(sex == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(sex == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(sex == 'TRUE') %>% select(n) +
                           dat %>% filter(sex == 'FALSE') %>% select(n)))

#############
### CASTE ###
#############

# check unique values
# unique(ea$ego_caste)
# unique(ea$alt_caste)

# set to numeric
ea$alt_caste <- as.numeric(ea$alt_caste)

# set don't know to NA
ea$alt_caste[ea$alt_caste == 9] <- NA

# summarise
caste <- ea$ego_caste == ea$alt_caste
dat <- tabyl(caste) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Caste (%)',
               value = dat %>% filter(caste == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(caste == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(caste == 'TRUE') %>% select(n) +
                           dat %>% filter(caste == 'FALSE') %>% select(n)))

#################
### EDUCATION ###
#################

# DON'T HAVE ALTER EDUCATION FROM EGO SURVEY !!!

################################
### NUMBER OF FAMILY MEMBERS ###
################################

# check unique values
# unique(ea$ego_fam)
# unique(ea$alt_fam)

# convert to numeric
ea$ego_fam <- as.numeric(ea$ego_fam)
ea$alt_fam <- as.numeric(ea$alt_fam)

# set don't know to NA
ea$alt_fam[ea$alt_fam == 99] <- NA

# # calculate bias homophily
# fam <- ea$ego_fam - ea$alt_fam
# fam <- tibble(mean_fam = mean(fam, na.rm = T),
#               med_fam = median(fam, na.rm = T),
#               n = length(fam[is.na(fam) == F]))

# create formula to calculate sd homophily
homo_sd <- function(ego, alt){
  out <- alt - ego
  out <- out*out
  n <- length(out[is.na(out) == F])
  out <- sum(out, na.rm = T)
  out <- out/n
  return(c(round(sqrt(out), 2), n))
}

# calculate sd homophily
fam_sd <- homo_sd(ea$ego_fam, ea$alt_fam)
dat <- tibble(aed = fam_sd[1],
                 n = fam_sd[2])

# add to homophily output
homo %<>% add_row(metric = 'Number of Family Members (AED)',
               value = dat %>% select(aed) %>% as.character,
               N = dat %>% select(n) %>% as.character)

#######################################
### NUMBER OF FRIENDS AND NEIGHBORS ###
#######################################

# check unique values
# unique(ea$ego_friends)
# unique(ea$alt_friends)
# unique(ea$ego_neigh)
# unique(ea$alt_neigh)

# convert to numeric
ea$ego_friends <- as.numeric(ea$ego_friends)
ea$alt_friends <- as.numeric(ea$alt_friends)
ea$ego_neigh <- as.numeric(ea$ego_neigh)
ea$alt_neigh <- as.numeric(ea$alt_neigh)

# set don't know to NA
ea$alt_friends[ea$alt_friends == 99] <- NA
ea$alt_neigh[ea$alt_neigh == 99] <- NA

# # calculate homophily
# friends <- ea$ego_friends - ea$alt_friends
# neigh <- ea$ego_neigh - ea$alt_neigh
# friends_neigh <- (ea$ego_friends + ea$ego_neigh) - (ea$alt_friends + ea$alt_neigh)
# 
# friends_neigh <- tibble(mean_friends = mean(friends, na.rm = T),
#                         med_friends = median(friends, na.rm = T),
#                         n_friends = length(friends[is.na(friends) == F]),
#                         mean_neigh = mean(neigh, na.rm = T),
#                         med_neigh = median(neigh, na.rm = T),
#                         n_neigh = length(neigh[is.na(neigh) == F]),
#                         mean_friends_neigh = mean(friends_neigh, na.rm = T),
#                         med_friends_neigh = median(friends_neigh, na.rm = T),
#                         n_friends_neigh = length(friends_neigh[is.na(friends_neigh) == F]))
# 
# write.csv(friends_neigh, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/homophily/ego_friends_neighbors_bias.csv',
#           row.names = F)

# calculate sd homophily
friends_sd <- homo_sd(ea$ego_friends, ea$alt_friends)
neigh_sd <- homo_sd(ea$ego_neigh, ea$alt_neigh)
friends_neigh_sd <- homo_sd((ea$ego_friends + ea$ego_neigh), (ea$alt_friends + ea$alt_neigh))
dat <- tibble(aed_friends = friends_sd[1],
                               n_friends = friends_sd[2],
                               aed_neigh = neigh_sd[1],
                               n_neigh = neigh_sd[2],
                               aed_friends_neigh = friends_neigh_sd[1],
                               n_friends_neigh = friends_neigh_sd[2])

# add to homophily output
homo %<>% add_row(metric = 'Number of Friends (AED)',
               value = dat %>% select(aed_friends) %>% as.character,
               N = dat %>% select(n_friends) %>% as.character) %>%
  add_row(metric = 'Number of Neighbors (AED)',
               value = dat %>% select(aed_neigh) %>% as.character,
               N = dat %>% select(n_neigh) %>% as.character) %>%
  add_row(metric = 'Number of Friends & Neighbors Combined (AED)',
               value = dat %>% select(aed_friends_neigh) %>% as.character,
               N = dat %>% select(n_friends_neigh) %>% as.character)

#####################
### PRACTICING FP ###
#####################

# PC ego values
# 1-10 are modern
# 11, 12, 96 are traditional
# 0 are missing

# alt values
# 1 = Yes, 2 = No, 9 = Don't Know

# check unique values
# unique(ea$ego_using_fp)
# unique(ea$alt_using_fp)

# set ego values to modern only is 1, 0 is not using any FP, so 2
ea %<>% mutate(ego_using_fp = replace(ego_using_fp, ego_using_fp %in% c(1:10, 95), 1))
ea %<>% mutate(ego_using_fp = replace(ego_using_fp, ego_using_fp %in% c(0, 11, 12), 2))

# set values to numeric
ea$alt_using_fp <- as.numeric(ea$alt_using_fp)

# if alter is husband change to same value as ego
ea$alt_using_fp[str_detect(ea$alt_relationship, 'Husband')] <- ea$ego_using_fp[str_detect(ea$alt_relationship, 'Husband')]

# set don't know to NA
ea$alt_using_fp[ea$alt_using_fp == 9] <- NA

# calculate homophily
using_fp <- ea$ego_using_fp == ea$alt_using_fp
dat <- tabyl(using_fp) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Currently Using Family Planning (%)',
               value = dat %>% filter(using_fp == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(using_fp == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(using_fp == 'TRUE') %>% select(n) +
                           dat %>% filter(using_fp == 'FALSE') %>% select(n)))

###############################
### PEOPLE KNOWN IN VILLAGE ###
###############################

# check some values
# unique(ea$ego_know_asha)
# unique(ea$alt_know_asha)

# for ego, 1 is Yes, 2 is heard, 9 is don't know/haven't heard
# for alter 1 is Yes, 2 is No, 9 is not sure
# we should change ego values of 9 to 2 to match alter
# remove alter rows with 9

# do individuals first
# asha
# recode values
ea$ego_know_asha[ea$ego_know_asha == '9'] <- '2'
ea$alt_know_asha[ea$alt_know_asha == '9'] <- NA

# calculate homophily
asha <- ea$ego_know_asha == ea$alt_know_asha
dat <- tabyl(asha) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Know ASHA (%)',
               value = dat %>% filter(asha == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(asha == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(asha == 'TRUE') %>% select(n) +
                           dat %>% filter(asha == 'FALSE') %>% select(n)))
# anm
# recode values
ea$ego_know_anm[ea$ego_know_anm == '9'] <- '2'
ea$alt_know_anm[ea$alt_know_anm == '9'] <- NA

# calculate homophily
anm <- ea$ego_know_anm == ea$alt_know_anm
dat <- tabyl(anm) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Know ANM (%)',
               value = dat %>% filter(anm == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(anm == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(anm == 'TRUE') %>% select(n) +
                           dat %>% filter(anm == 'FALSE') %>% select(n)))

# aww
# recode values
ea$ego_know_aww[ea$ego_know_aww == '9'] <- '2'
ea$alt_know_aww[ea$alt_know_aww == '9'] <- NA

# calculate homophily
aww <- ea$ego_know_aww == ea$alt_know_aww
dat <- tabyl(aww) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Know AWW (%)',
               value = dat %>% filter(aww == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(aww == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(aww == 'TRUE') %>% select(n) +
                           dat %>% filter(aww == 'FALSE') %>% select(n)))

# shg
# recode values
ea$ego_know_shg[ea$ego_know_shg == '9'] <- '2'
ea$alt_know_shg[ea$alt_know_shg == '9'] <- NA

# calculate homophily
shg <- ea$ego_know_shg == ea$alt_know_shg
dat <- tabyl(shg) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Know SHG (%)',
               value = dat %>% filter(shg == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(shg == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(shg == 'TRUE') %>% select(n) +
                           dat %>% filter(shg == 'FALSE') %>% select(n)))

# pradhan
# recode values
ea$ego_know_pra[ea$ego_know_pra == '9'] <- '2'
ea$alt_know_pra[ea$alt_know_pra == '9'] <- NA

# calculate homophily
pra <- ea$ego_know_pra == ea$alt_know_pra
dat <- tabyl(pra) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Know Pradhan (%)',
               value = dat %>% filter(pra == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(pra == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(pra == 'TRUE') %>% select(n) +
                           dat %>% filter(pra == 'FALSE') %>% select(n)))

# pharmacist
# recode values
ea$ego_know_pha[ea$ego_know_pha == '9'] <- '2'
ea$alt_know_pha[ea$alt_know_pha == '9'] <- NA

# calculate homophily
pha <- ea$ego_know_pha == ea$alt_know_pha
dat <- tabyl(pha) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Know Pharmacist (%)',
               value = dat %>% filter(pha == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(pha == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(pha == 'TRUE') %>% select(n) +
                           dat %>% filter(pha == 'FALSE') %>% select(n)))

# doctor
# recode values
ea$ego_know_doc[ea$ego_know_doc == '9'] <- '2'
ea$alt_know_doc[ea$alt_know_doc == '9'] <- NA

# calculate homophily
doc <- ea$ego_know_doc == ea$alt_know_doc
dat <- tabyl(doc) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Know Doctor (%)',
               value = dat %>% filter(doc == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(doc == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(doc == 'TRUE') %>% select(n) +
                           dat %>% filter(doc == 'FALSE') %>% select(n)))

# religious leader
# recode values
ea$ego_know_rel[ea$ego_know_rel == '9'] <- '2'
ea$alt_know_rel[ea$alt_know_rel == '9'] <- NA

# calculate homophily
rel <- ea$ego_know_rel == ea$alt_know_rel
dat <- tabyl(rel) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Know Religious Leader (%)',
               value = dat %>% filter(rel == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(rel == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(rel == 'TRUE') %>% select(n) +
                           dat %>% filter(rel == 'FALSE') %>% select(n)))

# now by category
# first all values to numeric
ea %<>% mutate(across(c(ego_know_asha,
                       ego_know_anm,
                       ego_know_aww,
                       ego_know_shg,
                       ego_know_pra,
                       ego_know_pha,
                       ego_know_doc,
                       ego_know_rel,
                       alt_know_asha,
                       alt_know_anm,
                       alt_know_aww,
                       alt_know_shg,
                       alt_know_pra,
                       alt_know_pha,
                       alt_know_doc,
                       alt_know_rel), as.numeric))

# exchange 2s for 0s
ea %<>% mutate(across(c(ego_know_asha,
                        ego_know_anm,
                        ego_know_aww,
                        ego_know_shg,
                        ego_know_pra,
                        ego_know_pha,
                        ego_know_doc,
                        ego_know_rel,
                        alt_know_asha,
                        alt_know_anm,
                        alt_know_aww,
                        alt_know_shg,
                        alt_know_pra,
                        alt_know_pha,
                        alt_know_doc,
                        alt_know_rel),
                      ~ ifelse(. == 2, 0, .)))

# calculate health worker category
ego_hw <- ea %>% 
  select(ego_know_asha,
         ego_know_anm,
         ego_know_aww,
         ego_know_pha,
         ego_know_doc) %>%
  rowSums(na.rm = T)

ego_hw <- ego_hw > 0

alt_hw <- ea %>% 
  select(alt_know_asha,
         alt_know_anm,
         alt_know_aww,
         alt_know_pha,
         alt_know_doc) %>%
  rowSums(na.rm = T)

alt_hw <- alt_hw > 0

# calculate homophily
hw <- ego_hw == alt_hw
dat <- tabyl(hw) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Know Health Worker Category (%)',
               value = dat %>% filter(hw == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(hw == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(hw == 'TRUE') %>% select(n) +
                           dat %>% filter(hw == 'FALSE') %>% select(n)))

# calculate village leader category
ego_vl <- ea %>% 
  select(ego_know_pra,
         ego_know_rel) %>%
  rowSums(na.rm = T)

ego_vl <- ego_vl > 0

alt_vl <- ea %>% 
  select(alt_know_pra,
         alt_know_rel) %>%
  rowSums(na.rm = T)

alt_vl <- alt_vl > 0

# calculate homophily
vl <- ego_vl == alt_vl
dat <- tabyl(vl) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Know Village Leader Category (%)',
               value = dat %>% filter(vl == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(vl == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(vl == 'TRUE') %>% select(n) +
                           dat %>% filter(vl == 'FALSE') %>% select(n)))

# now total number of people
ego_ppl <- ea %>%
  select(ego_know_asha,
         ego_know_anm,
         ego_know_aww,
         ego_know_shg,
         ego_know_pra,
         ego_know_pha,
         ego_know_doc,
         ego_know_rel) %>%
  rowSums(na.rm = T)

alt_ppl <- ea %>%
  select(alt_know_asha,
         alt_know_anm,
         alt_know_aww,
         alt_know_shg,
         alt_know_pra,
         alt_know_pha,
         alt_know_doc,
         alt_know_rel) %>%
  rowSums(na.rm = T)

# # calculate bias homophily
# ppl <- ego_ppl - alt_ppl
# ppl <- tibble(mean_people_known_village = mean(ppl, na.rm = T),
#               med_people_known_village = median(ppl, na.rm = T),
#               n = length(ppl[is.na(ppl) == F]))
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/homophily/ego_num_people_known_village_bias.csv',
#           row.names = F)

# calculate sd homophily
ppl_sd <- homo_sd(ego_ppl, alt_ppl)
dat <- tibble(aed = ppl_sd[1],
                 n = ppl_sd[2])

# add to homophily output
homo %<>% add_row(metric = 'Total Number of Important People Known (AED)',
               value = dat %>% select(aed) %>% as.character,
               N = dat %>% select(n) %>% as.character)

##########################
### NUMBER OF CHILDREN ###
##########################

# check unique values
# unique(ea$ego_sons)
# unique(ea$alt_sons)
# unique(ea$ego_daughters)
# unique(ea$alt_daughters)

# change husband values to same as ego
ea$alt_sons[ea$alt_relationship == "Husband "] <- ea$ego_sons[ea$alt_relationship == "Husband "]
ea$alt_daughters[ea$alt_relationship == "Husband "] <- ea$ego_daughters[ea$alt_relationship == "Husband "]

# convert to numeric
ea$ego_sons <- as.numeric(ea$ego_sons)
ea$alt_sons <- as.numeric(ea$alt_sons)
ea$ego_daughters <- as.numeric(ea$ego_daughters)
ea$alt_daughters <- as.numeric(ea$alt_daughters)

# set don't know to NA
ea$alt_sons[ea$alt_sons == 99] <- NA
ea$alt_daughters[ea$alt_daughters == 99] <- NA

# # calculate bias homophily
# sons <- ea$ego_sons - ea$alt_sons
# daughters <- ea$ego_daughters - ea$alt_daughters
# children <- (ea$ego_sons + ea$ego_daughters) - (ea$alt_sons + ea$alt_daughters)
# 
# children_bias <- tibble(mean_sons = mean(sons, na.rm = T),
#                         med_sons = median(sons, na.rm = T),
#                         n_sons = length(sons[is.na(sons) == F]),
#                         mean_daughters = mean(daughters, na.rm = T),
#                         med_daughters = median(daughters, na.rm = T),
#                         n_daughters = length(neigh[is.na(daughters) == F]),
#                         mean_children = mean(children, na.rm = T),
#                         med_children = median(children, na.rm = T),
#                         n_children = length(children[is.na(children) == F]))

# calculate sd homophily
sons_sd <- homo_sd(ea$ego_sons, ea$alt_sons)
daughters_sd <- homo_sd(ea$ego_daughters, ea$alt_daughters)
children_sd <- homo_sd((ea$ego_sons + ea$ego_daughters), (ea$alt_sons + ea$alt_daughters))
dat <- tibble(aed_sons = sons_sd[1],
                               n_sons = sons_sd[2],
                               aed_daughters = daughters_sd[1],
                               n_daughters = daughters_sd[2],
                               aed_children = children_sd[1],
                               n_children = children_sd[2])

# add to homophily output
homo %<>% add_row(metric = 'Number of Sons (AED)',
               value = dat %>% select(aed_sons) %>% as.character,
               N = dat %>% select(n_sons) %>% as.character) %>%
  add_row(metric = 'Number of Daughters (AED)',
               value = dat %>% select(aed_daughters) %>% as.character,
               N = dat %>% select(n_daughters) %>% as.character) %>%
  add_row(metric = 'Number of Children Total (AED)',
               value = dat %>% select(aed_children) %>% as.character,
               N = dat %>% select(n_children) %>% as.character)

##############################################
### BASIC PROPORTION OF PLACE OF RESIDENCE ###
##############################################

# check unique values
# unique(ea$alt_residence)

# recode values
ea %<>% mutate(alt_residence = recode(alt_residence, 
                                     '1' = 'Same Household',
                                     '2' = 'Same Village',
                                     '3' = 'Another Village (same district)',
                                     '4' = 'Outside this District'))

# build tabyl
dat <- ea %>% tabyl(alt_residence) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo %<>% add_row(metric = 'Live in Same Household (%)',
               value = dat %>% filter(alt_residence == 'Same Household') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(alt_residence == 'Same Household') %>% select(n),
                         '/',
                         dat %>% select(n) %>% sum)) %>%
  add_row(metric = 'Live in Same Village (%)',
               value = dat %>% filter(alt_residence == 'Same Village') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(alt_residence == 'Same Village') %>% select(n),
                         '/',
                         dat %>% select(n) %>% sum)) %>%
  add_row(metric = 'Live in Another Village, Same District (%)',
               value = dat %>% filter(alt_residence == 'Another Village (same district)') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(alt_residence == 'Another Village (same district)') %>% select(n),
                         '/',
                         dat %>% select(n) %>% sum)) %>%
  add_row(metric = 'Live in Another District (%)',
               value = dat %>% filter(alt_residence == 'Outside this District') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(alt_residence == 'Outside this District') %>% select(n),
                         '/',
                         dat %>% select(n) %>% sum))

```

```{r, echo = F, warning = F, message = F, results = 'asis'}
#####################################
### HETEROGENEITY OF EGO'S ALTERS ###
#####################################

###########
### SEX ###
###########

# check unique values
# unique(ea$alt_sex)

# build proportions
sex <- ea %>% tabyl(alt_sex)

# create a function to calculate blaus and iqv
blau <- function(perc){
  b <- perc*perc
  k <- length(perc)
  b <- (1 - sum(b)) %>% round(2)
  iqv <- (b / (1-(1/k))) %>% round(2)
  return(c(b, iqv, k))
}

if('valid_percent' %in% colnames(sex)){
  sex %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- sex$n[is.na(sex$percent) == F] %>% sum

# calculate heterogeneity
sex <- blau(na.omit(sex$percent))

# create tibble
dat = tibble(blau = sex[1],
             iqv = sex[2],
             k = sex[3])

# create heterogeneity output
hetero <- tibble(metric = 'Gender',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

#############
### CASTE ###
#############

# check unique values
# unique(ea$alt_caste)

# build proportions
caste <- ea %>% tabyl(alt_caste)

if('valid_percent' %in% colnames(caste)){
  caste %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- caste$n[is.na(caste$percent) == F] %>% sum

# calculate heterogeneity
caste <- blau(na.omit(caste$percent))

# create tibble
dat = tibble(blau = caste[1],
             iqv = caste[2],
             k = caste[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Caste',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

################################
### NUMBER OF FAMILY MEMBERS ###
################################

# check unique values
# unique(ea$alt_fam)

# # calculate heterogeneity
# fam <- tibble(fam_sd = sd(ea$alt_fam, na.rm = T) %>% round(2),
#               n = length(ea$alt_fam[is.na(ea$alt_fam) == F]))

#######################################
### NUMBER OF FRIENDS AND NEIGHBORS ###
#######################################

# check unique values
# unique(ea$alt_friends)
# unique(ea$alt_neigh)

# # calculate heterogeneity
# friends_neigh <- tibble(friends_sd = sd(ea$alt_friends, na.rm = T) %>% round(2),
#               friends_n = length(ea$alt_friends[is.na(ea$alt_friends) == F]),
#               neigh_sd = sd(ea$alt_neigh, na.rm = T) %>% round(2),
#               neigh_n = length(ea$alt_neigh[is.na(ea$alt_neigh) == F]),
#               friends_neigh_sd = sd((ea$alt_friends + ea$alt_neigh), na.rm = T) %>% round(2),
#               friends_neigh_n = length((ea$alt_friends + ea$alt_neigh)[is.na((ea$alt_friends + ea$alt_neigh)) == F]))

#####################
### PRACTICING FP ###
#####################

# PC ego values
# 1 = Yes, 2 = No

# alt values
# 1 = Yes, 2 = No, 9 = Don't Know

# check unique values
# unique(ea$alt_using_fp)

# calculate heterogeneity
using_fp <- tabyl(ea$alt_using_fp)

if('valid_percent' %in% colnames(using_fp)){
  using_fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- using_fp$n[is.na(using_fp$percent) == F] %>% sum
using_fp <- blau(na.omit(using_fp$percent))
dat <- tibble(blau = using_fp[1],
                   iqv = using_fp[2],
                   k = using_fp[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Currently Using Family Planning',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

###############################
### PEOPLE KNOWN IN VILLAGE ###
###############################

# check some values
# unique(ea$alt_know_asha)

# for ego, 1 is Yes, 2 is heard, 9 is don't know/haven't heard
# for alter 1 is Yes, 2 is No, 9 is not sure
# we should change ego values of 9 to 2 to match alter
# remove alter rows with 9

# calculate heterogeneity
ppl <- tabyl(ea$alt_know_asha)

if('valid_percent' %in% colnames(ppl)){
  ppl %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- ppl$n[is.na(ppl$percent) == F] %>% sum
ppl <- blau(na.omit(ppl$percent))
dat <- tibble(blau = ppl[1],
              iqv = ppl[2],
              k = ppl[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Know ASHA',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

# anm
# calculate heterogeneity
ppl <- tabyl(ea$alt_know_anm)

if('valid_percent' %in% colnames(ppl)){
  ppl %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- ppl$n[is.na(ppl$percent) == F] %>% sum
ppl <- blau(na.omit(ppl$percent))
dat <- tibble(blau = ppl[1],
              iqv = ppl[2],
              k = ppl[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Know ANM',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

# aww
# calculate heterogeneity
ppl <- tabyl(ea$alt_know_aww)

if('valid_percent' %in% colnames(ppl)){
  ppl %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- ppl$n[is.na(ppl$percent) == F] %>% sum
ppl <- blau(na.omit(ppl$percent))
dat <- tibble(blau = ppl[1],
              iqv = ppl[2],
              k = ppl[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Know AWW',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

# shg
# calculate heterogeneity
ppl <- tabyl(ea$alt_know_shg)

if('valid_percent' %in% colnames(ppl)){
  ppl %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- ppl$n[is.na(ppl$percent) == F] %>% sum
ppl <- blau(na.omit(ppl$percent))
dat <- tibble(blau = ppl[1],
              iqv = ppl[2],
              k = ppl[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Know SHG',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

# pradhan
# calculate heterogeneity
ppl <- tabyl(ea$alt_know_pra)

if('valid_percent' %in% colnames(ppl)){
  ppl %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- ppl$n[is.na(ppl$percent) == F] %>% sum
ppl <- blau(na.omit(ppl$percent))
dat <- tibble(blau = ppl[1],
              iqv = ppl[2],
              k = ppl[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Know Pradhan',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

# pharmacist
# calculate heterogeneity
ppl <- tabyl(ea$alt_know_pha)

if('valid_percent' %in% colnames(ppl)){
  ppl %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- ppl$n[is.na(ppl$percent) == F] %>% sum
ppl <- blau(na.omit(ppl$percent))
dat <- tibble(blau = ppl[1],
              iqv = ppl[2],
              k = ppl[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Know Pharmacist',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

# doctor
# calculate heterogeneity
ppl <- tabyl(ea$alt_know_doc)

if('valid_percent' %in% colnames(ppl)){
  ppl %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- ppl$n[is.na(ppl$percent) == F] %>% sum
ppl <- blau(na.omit(ppl$percent))
dat <- tibble(blau = ppl[1],
              iqv = ppl[2],
              k = ppl[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Know Doctor',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

# religious leader
# calculate heterogeneity
ppl <- tabyl(ea$alt_know_rel)

if('valid_percent' %in% colnames(ppl)){
  ppl %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- ppl$n[is.na(ppl$percent) == F] %>% sum
ppl <- blau(na.omit(ppl$percent))
dat <- tibble(blau = ppl[1],
              iqv = ppl[2],
              k = ppl[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Know Religious Leader',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

# calculate health worker category


# calculate homophily
# calculate heterogeneity
ppl <- tabyl(alt_hw)

if('valid_percent' %in% colnames(ppl)){
  ppl %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- ppl$n[is.na(ppl$percent) == F] %>% sum
ppl <- blau(na.omit(ppl$percent))
dat <- tibble(blau = ppl[1],
              iqv = ppl[2],
              k = ppl[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Know Health Worker Category',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

# calculate village leader category
# calculate heterogeneity
ppl <- tabyl(alt_vl)

if('valid_percent' %in% colnames(ppl)){
  ppl %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- ppl$n[is.na(ppl$percent) == F] %>% sum
ppl <- blau(na.omit(ppl$percent))
dat <- tibble(blau = ppl[1],
              iqv = ppl[2],
              k = ppl[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Know Village Leader Category',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

# # now total number of people
# # calculate heterogeneity
# ppl <- tibble(ppl_known_village_sd = sd(alt_ppl, na.rm = T) %>% round(2),
#               n = length(alt_ppl[is.na(alt_ppl) == F]))

##########################
### NUMBER OF CHILDREN ###
##########################

# check unique values
# unique(ea$alt_sons)
# unique(ea$alt_daughters)

# # calculate heterogeneity
# children <- tibble(sons_sd = sd(ea$alt_sons, na.rm = T) %>% round(2),
#               sons_n = length(ea$alt_sons[is.na(ea$alt_sons) == F]),
#               daughters_sd = sd(ea$alt_daughters, na.rm = T) %>% round(2),
#               daughters_n = length(ea$alt_daughters[is.na(ea$alt_daughters) == F]),
#               children_sd = sd((ea$alt_sons + ea$alt_daughters), na.rm = T) %>% round(2),
#               children_n = length((ea$alt_sons + ea$alt_daughters)[is.na((ea$alt_sons + ea$alt_daughters)) == F]))

##########################
### PLACE OF RESIDENCE ###
##########################

# check unique values
# unique(ea$alt_residence)

# calculate heterogeneity
res <- tabyl(ea$alt_residence)

if('valid_percent' %in% colnames(res)){
  res %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- res$n[is.na(res$percent) == F] %>% sum
res <- blau(na.omit(res$percent))
dat <- tibble(blau = res[1],
              iqv = res[2],
              k = res[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Residence',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

#######################
### SOCIAL LEARNING ###
#######################

# check unique values
#unique(ea$alt_learned)

# calculate homophily
a <- tabyl(str_detect(ea$alt_learned, "A"))

if('valid_percent' %in% colnames(a)){
  a %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- a$n[is.na(a$percent) == F] %>% sum
a <- blau(na.omit(a$percent))
dat <- tibble(blau = a[1],
              iqv = a[2],
              k = a[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Social Learning: Get along with family',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

b <- tabyl(str_detect(ea$alt_learned, "B"))

if('valid_percent' %in% colnames(b)){
  b %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- b$n[is.na(b$percent) == F] %>% sum
b <- blau(na.omit(b$percent))
dat <- tibble(blau = b[1],
              iqv = b[2],
              k = b[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Social Learning: Ways of earning',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

c <- tabyl(str_detect(ea$alt_learned, "C"))

if('valid_percent' %in% colnames(c)){
  c %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- c$n[is.na(c$percent) == F] %>% sum
c <- blau(na.omit(c$percent))
dat <- tibble(blau = c[1],
              iqv = c[2],
              k = c[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Social Learning: Take care of children',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

d <- tabyl(str_detect(ea$alt_learned, "D"))

if('valid_percent' %in% colnames(d)){
  d %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- d$n[is.na(d$percent) == F] %>% sum
d <- blau(na.omit(d$percent))
dat <- tibble(blau = d[1],
              iqv = d[2],
              k = d[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Social Learning: Get health care',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

e <- tabyl(str_detect(ea$alt_learned, "E"))

if('valid_percent' %in% colnames(e)){
  e %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- e$n[is.na(e$percent) == F] %>% sum
e <- blau(na.omit(e$percent))
dat <- tibble(blau = e[1],
              iqv = e[2],
              k = e[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Social Learning: Apply for government schemes',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

f <- tabyl(str_detect(ea$alt_learned, "F"))

if('valid_percent' %in% colnames(f)){
  f %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- f$n[is.na(f$percent) == F] %>% sum
f <- blau(na.omit(f$percent))
dat <- tibble(blau = f[1],
              iqv = f[2],
              k = f[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Social Learning: Plan no. of children to have',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

g <- tabyl(str_detect(ea$alt_learned, "G"))

if('valid_percent' %in% colnames(g)){
  g %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- g$n[is.na(g$percent) == F] %>% sum
g <- blau(na.omit(g$percent))
dat <- tibble(blau = g[1],
              iqv = g[2],
              k = g[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Social Learning: FP methods',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

###########################
### ENCOURAGE USE OF FP ###
###########################

# check unique values
# unique(ea$alt_encourage_fp)

# calculate heterogeneity
fp <- tabyl(ea$alt_encourage_fp)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
              iqv = fp[2],
              k = fp[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Encourage Use of Family Planning',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

#################################
### DISCUSS FP METHODS FREELY ###
#################################

# check unique values
# unique(ea$alt_discuss_fp)

# calculate heterogeneity
fp <- tabyl(ea$alt_discuss_fp)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
             iqv = fp[2],
             k = fp[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Discuss FP Methods Freely',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

###########################
### ALT HELP/ADVISE EGO ###
###########################

# check unique values
# unique(ea$alt_help_ego)

# calculate heterogeneity
fp <- tabyl(ea$alt_help_ego)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
             iqv = fp[2],
             k = fp[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Alter Help/Advise Ego',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

###########################
### EGO HELP/ADVISE ALT ###
###########################

# check unique values
# unique(ea$alt_helped_by_ego)

# calculate heterogeneity
fp <- tabyl(ea$alt_helped_by_ego)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
             iqv = fp[2],
             k = fp[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Ego Help/Advise Alter',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

############################
### GOING AGAINST ADVICE ###
############################

# check unique values
# unique(ea$alt_against_advice)

# calculate heterogeneity
fp <- tabyl(ea$alt_against_advice)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
             iqv = fp[2],
             k = fp[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Going Against Advice',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

###################################
### SUPPORT NOT HAVING CHILDREN ###
###################################

# check unique values
# unique(ea$alt_support_no_child)

# calculate heterogeneity
fp <- tabyl(ea$alt_support_no_child)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
             iqv = fp[2],
             k = fp[3])

# add to heterogeneity output
hetero %<>% add_row(metric = 'Support Not Having Children',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)
```

```{r, echo = F, warning = F, message = F, results = 'asis'}
#################################################################
### CALCULATE HOMOPHILY AND HETEROGENEITY OF ALTER AND AALTER ###
#################################################################

##################################
### HOMOPHILY ALTER AND AALTER ###
##################################

# gender
# education
# number of family members
# number of non-family members close to
# practicing FP
# network composition: family/non-family (?)

# sort ego data and PC data by woman ID so can merge
ego %<>% arrange(woman_id)
ego_pc %<>% arrange(qe6) # qe6 is woman_id

# make sure ego_ids match
# sum(ego_pc$qe6 == ego$woman_id)

# build tibble of ego and alter attributes since we might need some variables
ego_alter_old <- rbind(tibble(ego_id = ego$woman_id,
                              alter_name = ego$alter1,
                              alter_id = str_c(ego$woman_id, 1),
                              ego_sex = 2,
                              alt_sex = ego$alter1_sex,
                              ego_caste = ego_pc$pcq111,
                              alt_caste = ego$alter1_caste,
                              ego_edu = ego_pc$pcq103,
                              alt_edu = NA,
                              ego_fam = ego$family_members,
                              alt_fam = ego$alter1_family,
                              ego_friends = ego$friends,
                              alt_friends = ego$alter1_friends,
                              ego_neigh = ego$neighbours,
                              alt_neigh = ego$alter1_neighbours,
                              ego_using_fp = ego_pc$pcq312,
                              alt_using_fp = ego$alter1_using_fp,
                              ego_know_asha = ego$know_asha,
                              ego_know_anm = ego$know_anm,
                              ego_know_aww = ego$know_aww,
                              ego_know_shg = ego$know_shg,
                              ego_know_pra = ego$know_pradhan,
                              ego_know_pha = ego$know_pharmacist,
                              ego_know_doc = ego$know_doctor,
                              ego_know_rel = ego$know_religious_leader,
                              alt_know_asha = ego$alter1_asha,
                              alt_know_anm = ego$alter1_anm,
                              alt_know_aww = ego$alter1_aww,
                              alt_know_shg = ego$alter1_shg,
                              alt_know_pra = ego$alter1_pradhan,
                              alt_know_pha = ego$alter1_pharmacist,
                              alt_know_doc = ego$alter1_doctor,
                              alt_know_rel = ego$alter1_religious_leader,
                              ego_sons = ego_pc$pcq205s,
                              ego_daughters = ego_pc$pcq205d,
                              alt_sons = ego$alter1_sons,
                              alt_daughters = ego$alter1_daughters,
                              alt_residence = ego$alter1_residence,
                              alt_relationship = ego$alter1r,
                              alt_learned = ego$alter1_learned,
                              alt_encourage_fp = ego$alter1_encourage_fp,
                              alt_discuss_fp = ego$alter1_discuss_fp,
                              alt_help_ego = ego$alter1_help,
                              alt_helped_by_ego = ego$alter1_helped,
                              alt_against_advice = ego$alter1_follow_advice,
                              alt_support_no_child = ego$alter1_nochild),
                       tibble(ego_id = ego$woman_id,
                              alter_name = ego$alter2,
                              alter_id = str_c(ego$woman_id, 2),
                              ego_sex = 2,
                              alt_sex = ego$alter2_sex,
                              ego_caste = ego_pc$pcq111,
                              alt_caste = ego$alter2_caste,
                              ego_edu = ego_pc$pcq103,
                              alt_edu = NA,
                              ego_fam = ego$family_members,
                              alt_fam = ego$alter2_family,
                              ego_friends = ego$friends,
                              alt_friends = ego$alter2_friends,
                              ego_neigh = ego$neighbours,
                              alt_neigh = ego$alter2_neighbours,
                              ego_using_fp = ego_pc$pcq312,
                              alt_using_fp = ego$alter2_using_fp,
                              ego_know_asha = ego$know_asha,
                              ego_know_anm = ego$know_anm,
                              ego_know_aww = ego$know_aww,
                              ego_know_shg = ego$know_shg,
                              ego_know_pra = ego$know_pradhan,
                              ego_know_pha = ego$know_pharmacist,
                              ego_know_doc = ego$know_doctor,
                              ego_know_rel = ego$know_religious_leader,
                              alt_know_asha = ego$alter2_asha,
                              alt_know_anm = ego$alter2_anm,
                              alt_know_aww = ego$alter2_aww,
                              alt_know_shg = ego$alter2_shg,
                              alt_know_pra = ego$alter2_pradhan,
                              alt_know_pha = ego$alter2_pharmacist,
                              alt_know_doc = ego$alter2_doctor,
                              alt_know_rel = ego$alter2_religious_leader,
                              ego_sons = ego_pc$pcq205s,
                              ego_daughters = ego_pc$pcq205d,
                              alt_sons = ego$alter2_sons,
                              alt_daughters = ego$alter2_daughters,
                              alt_residence = ego$alter2_residence,
                              alt_relationship = ego$alter2r,
                              alt_learned = ego$alter2_learned,
                              alt_encourage_fp = ego$alter2_encourage_fp,
                              alt_discuss_fp = ego$alter2_discuss_fp,
                              alt_help_ego = ego$alter2_help,
                              alt_helped_by_ego = ego$alter2_helped,
                              alt_against_advice = ego$alter2_follow_advice,
                              alt_support_no_child = ego$alter2_nochild),
                       tibble(ego_id = ego$woman_id,
                              alter_name = ego$alter3,
                              alter_id = str_c(ego$woman_id, 3),
                              ego_sex = 2,
                              alt_sex = ego$alter3_sex,
                              ego_caste = ego_pc$pcq111,
                              alt_caste = ego$alter3_caste,
                              ego_edu = ego_pc$pcq103,
                              alt_edu = NA,
                              ego_fam = ego$family_members,
                              alt_fam = ego$alter3_family,
                              ego_friends = ego$friends,
                              alt_friends = ego$alter3_friends,
                              ego_neigh = ego$neighbours,
                              alt_neigh = ego$alter3_neighbours,
                              ego_using_fp = ego_pc$pcq312,
                              alt_using_fp = ego$alter3_using_fp,
                              ego_know_asha = ego$know_asha,
                              ego_know_anm = ego$know_anm,
                              ego_know_aww = ego$know_aww,
                              ego_know_shg = ego$know_shg,
                              ego_know_pra = ego$know_pradhan,
                              ego_know_pha = ego$know_pharmacist,
                              ego_know_doc = ego$know_doctor,
                              ego_know_rel = ego$know_religious_leader,
                              alt_know_asha = ego$alter3_asha,
                              alt_know_anm = ego$alter3_anm,
                              alt_know_aww = ego$alter3_aww,
                              alt_know_shg = ego$alter3_shg,
                              alt_know_pra = ego$alter3_pradhan,
                              alt_know_pha = ego$alter3_pharmacist,
                              alt_know_doc = ego$alter3_doctor,
                              alt_know_rel = ego$alter3_religious_leader,
                              ego_sons = ego_pc$pcq205s,
                              ego_daughters = ego_pc$pcq205d,
                              alt_sons = ego$alter3_sons,
                              alt_daughters = ego$alter3_daughters,
                              alt_residence = ego$alter3_residence,
                              alt_relationship = ego$alter3r,
                              alt_learned = ego$alter3_learned,
                              alt_encourage_fp = ego$alter3_encourage_fp,
                              alt_discuss_fp = ego$alter3_discuss_fp,
                              alt_help_ego = ego$alter3_help,
                              alt_helped_by_ego = ego$alter3_helped,
                              alt_against_advice = ego$alter3_follow_advice,
                              alt_support_no_child = ego$alter3_nochild),
                       tibble(ego_id = ego$woman_id,
                              alter_name = ego$alter4,
                              alter_id = str_c(ego$woman_id, 4),
                              ego_sex = 2,
                              alt_sex = ego$alter4_sex,
                              ego_caste = ego_pc$pcq111,
                              alt_caste = ego$alter4_caste,
                              ego_edu = ego_pc$pcq103,
                              alt_edu = NA,
                              ego_fam = ego$family_members,
                              alt_fam = ego$alter4_family,
                              ego_friends = ego$friends,
                              alt_friends = ego$alter4_friends,
                              ego_neigh = ego$neighbours,
                              alt_neigh = ego$alter4_neighbours,
                              ego_using_fp = ego_pc$pcq312,
                              alt_using_fp = ego$alter4_using_fp,
                              ego_know_asha = ego$know_asha,
                              ego_know_anm = ego$know_anm,
                              ego_know_aww = ego$know_aww,
                              ego_know_shg = ego$know_shg,
                              ego_know_pra = ego$know_pradhan,
                              ego_know_pha = ego$know_pharmacist,
                              ego_know_doc = ego$know_doctor,
                              ego_know_rel = ego$know_religious_leader,
                              alt_know_asha = ego$alter4_asha,
                              alt_know_anm = ego$alter4_anm,
                              alt_know_aww = ego$alter4_aww,
                              alt_know_shg = ego$alter4_shg,
                              alt_know_pra = ego$alter4_pradhan,
                              alt_know_pha = ego$alter4_pharmacist,
                              alt_know_doc = ego$alter4_doctor,
                              alt_know_rel = ego$alter4_religious_leader,
                              ego_sons = ego_pc$pcq205s,
                              ego_daughters = ego_pc$pcq205d,
                              alt_sons = ego$alter4_sons,
                              alt_daughters = ego$alter4_daughters,
                              alt_residence = ego$alter4_residence,
                              alt_relationship = ego$alter4r,
                              alt_learned = ego$alter4_learned,
                              alt_encourage_fp = ego$alter4_encourage_fp,
                              alt_discuss_fp = ego$alter4_discuss_fp,
                              alt_help_ego = ego$alter4_help,
                              alt_helped_by_ego = ego$alter4_helped,
                              alt_against_advice = ego$alter4_follow_advice,
                              alt_support_no_child = ego$alter4_nochild),
                       tibble(ego_id = ego$woman_id,
                              alter_name = ego$alter5,
                              alter_id = str_c(ego$woman_id, 5),
                              ego_sex = 2,
                              alt_sex = ego$alter5_sex,
                              ego_caste = ego_pc$pcq111,
                              alt_caste = ego$alter5_caste,
                              ego_edu = ego_pc$pcq103,
                              alt_edu = NA,
                              ego_fam = ego$family_members,
                              alt_fam = ego$alter5_family,
                              ego_friends = ego$friends,
                              alt_friends = ego$alter5_friends,
                              ego_neigh = ego$neighbours,
                              alt_neigh = ego$alter5_neighbours,
                              ego_using_fp = ego_pc$pcq312,
                              alt_using_fp = ego$alter5_using_fp,
                              ego_know_asha = ego$know_asha,
                              ego_know_anm = ego$know_anm,
                              ego_know_aww = ego$know_aww,
                              ego_know_shg = ego$know_shg,
                              ego_know_pra = ego$know_pradhan,
                              ego_know_pha = ego$know_pharmacist,
                              ego_know_doc = ego$know_doctor,
                              ego_know_rel = ego$know_religious_leader,
                              alt_know_asha = ego$alter5_asha,
                              alt_know_anm = ego$alter5_anm,
                              alt_know_aww = ego$alter5_aww,
                              alt_know_shg = ego$alter5_shg,
                              alt_know_pra = ego$alter5_pradhan,
                              alt_know_pha = ego$alter5_pharmacist,
                              alt_know_doc = ego$alter5_doctor,
                              alt_know_rel = ego$alter5_religious_leader,
                              ego_sons = ego_pc$pcq205s,
                              ego_daughters = ego_pc$pcq205d,
                              alt_sons = ego$alter5_sons,
                              alt_daughters = ego$alter5_daughters,
                              alt_residence = ego$alter5_residence,
                              alt_relationship = ego$alter5r,
                              alt_learned = ego$alter5_learned,
                              alt_encourage_fp = ego$alter5_encourage_fp,
                              alt_discuss_fp = ego$alter5_discuss_fp,
                              alt_help_ego = ego$alter5_help,
                              alt_helped_by_ego = ego$alter5_helped,
                              alt_against_advice = ego$alter5_follow_advice,
                              alt_support_no_child = ego$alter5_nochild))

# drop rows for missing alters
ego_alter_old %<>% filter(is.na(alter_name) == F)

# build tibble of alter and aalter attributes
ea <- rbind(tibble(ego_id = alter$alter_id,
                   alter_name = alter$alter1,
                   ego_sex = NA,
                   alt_sex = alter$alter1_sex,
                   ego_caste = alter$caste,
                   alt_caste = alter$alter1_caste,
                   ego_edu = alter$education,
                   alt_edu = NA,
                   ego_fam = alter$family_members,
                   alt_fam = alter$alter1_family,
                   ego_friends = alter$friends,
                   alt_friends = alter$alter1_friends,
                   ego_neigh = alter$neighbours,
                   alt_neigh = alter$alter1_neighbours,
                   ego_using_fp = alter$current_method,
                   alt_using_fp = alter$alter1_using_fp,
                   ego_know_asha = alter$know_asha,
                   ego_know_anm = alter$know_anm,
                   ego_know_aww = alter$know_aww,
                   ego_know_shg = alter$know_shg,
                   ego_know_pra = alter$know_pradhan,
                   ego_know_pha = alter$know_pharmacist,
                   ego_know_doc = alter$know_doctor,
                   ego_know_rel = alter$know_religious_leader,
                   alt_know_asha = NA,
                   alt_know_anm = NA,
                   alt_know_aww = NA,
                   alt_know_shg = NA,
                   alt_know_pra = NA,
                   alt_know_pha = NA,
                   alt_know_doc = NA,
                   alt_know_rel = NA,
                   ego_sons = alter$sons,
                   ego_daughters = alter$daughters,
                   alt_sons = alter$alter1_sons,
                   alt_daughters = alter$alter1_daughters,
                   alt_residence = alter$alter1_residence,
                   alt_relationship = alter$alter1r,
                   alt_learned = alter$alter1_learned,
                   alt_encourage_fp = alter$alter1_encourage_fp,
                   alt_discuss_fp = alter$alter1_discuss_fp,
                   alt_help_ego = alter$alter1_help,
                   alt_helped_by_ego = alter$alter1_helped,
                   alt_against_advice = alter$alter1_follow_advice,
                   alt_support_no_child = alter$alter1_nochild),
            tibble(ego_id = alter$alter_id,
                   alter_name = alter$alter2,
                   ego_sex = NA,
                   alt_sex = alter$alter2_sex,
                   ego_caste = alter$caste,
                   alt_caste = alter$alter2_caste,
                   ego_edu = alter$education,
                   alt_edu = NA,
                   ego_fam = alter$family_members,
                   alt_fam = alter$alter2_family,
                   ego_friends = alter$friends,
                   alt_friends = alter$alter2_friends,
                   ego_neigh = alter$neighbours,
                   alt_neigh = alter$alter2_neighbours,
                   ego_using_fp = alter$current_method,
                   alt_using_fp = alter$alter2_using_fp,
                   ego_know_asha = alter$know_asha,
                   ego_know_anm = alter$know_anm,
                   ego_know_aww = alter$know_aww,
                   ego_know_shg = alter$know_shg,
                   ego_know_pra = alter$know_pradhan,
                   ego_know_pha = alter$know_pharmacist,
                   ego_know_doc = alter$know_doctor,
                   ego_know_rel = alter$know_religious_leader,
                   alt_know_asha = NA,
                   alt_know_anm = NA,
                   alt_know_aww = NA,
                   alt_know_shg = NA,
                   alt_know_pra = NA,
                   alt_know_pha = NA,
                   alt_know_doc = NA,
                   alt_know_rel = NA,
                   ego_sons = alter$sons,
                   ego_daughters = alter$daughters,
                   alt_sons = alter$alter2_sons,
                   alt_daughters = alter$alter2_daughters,
                   alt_residence = alter$alter2_residence,
                   alt_relationship = alter$alter2r,
                   alt_learned = alter$alter2_learned,
                   alt_encourage_fp = alter$alter2_encourage_fp,
                   alt_discuss_fp = alter$alter2_discuss_fp,
                   alt_help_ego = alter$alter2_help,
                   alt_helped_by_ego = alter$alter2_helped,
                   alt_against_advice = alter$alter2_follow_advice,
                   alt_support_no_child = alter$alter2_nochild),
            tibble(ego_id = alter$alter_id,
                   alter_name = alter$alter3,
                   ego_sex = NA,
                   alt_sex = alter$alter3_sex,
                   ego_caste = alter$caste,
                   alt_caste = alter$alter3_caste,
                   ego_edu = alter$education,
                   alt_edu = NA,
                   ego_fam = alter$family_members,
                   alt_fam = alter$alter3_family,
                   ego_friends = alter$friends,
                   alt_friends = alter$alter3_friends,
                   ego_neigh = alter$neighbours,
                   alt_neigh = alter$alter3_neighbours,
                   ego_using_fp = alter$current_method,
                   alt_using_fp = alter$alter3_using_fp,
                   ego_know_asha = alter$know_asha,
                   ego_know_anm = alter$know_anm,
                   ego_know_aww = alter$know_aww,
                   ego_know_shg = alter$know_shg,
                   ego_know_pra = alter$know_pradhan,
                   ego_know_pha = alter$know_pharmacist,
                   ego_know_doc = alter$know_doctor,
                   ego_know_rel = alter$know_religious_leader,
                   alt_know_asha = NA,
                   alt_know_anm = NA,
                   alt_know_aww = NA,
                   alt_know_shg = NA,
                   alt_know_pra = NA,
                   alt_know_pha = NA,
                   alt_know_doc = NA,
                   alt_know_rel = NA,
                   ego_sons = alter$sons,
                   ego_daughters = alter$daughters,
                   alt_sons = alter$alter3_sons,
                   alt_daughters = alter$alter3_daughters,
                   alt_residence = alter$alter3_residence,
                   alt_relationship = alter$alter3r,
                   alt_learned = alter$alter3_learned,
                   alt_encourage_fp = alter$alter3_encourage_fp,
                   alt_discuss_fp = alter$alter3_discuss_fp,
                   alt_help_ego = alter$alter3_help,
                   alt_helped_by_ego = alter$alter3_helped,
                   alt_against_advice = alter$alter3_follow_advice,
                   alt_support_no_child = alter$alter3_nochild),
            tibble(ego_id = alter$alter_id,
                   alter_name = alter$alter4,
                   ego_sex = NA,
                   alt_sex = alter$alter4_sex,
                   ego_caste = alter$caste,
                   alt_caste = alter$alter4_caste,
                   ego_edu = alter$education,
                   alt_edu = NA,
                   ego_fam = alter$family_members,
                   alt_fam = alter$alter4_family,
                   ego_friends = alter$friends,
                   alt_friends = alter$alter4_friends,
                   ego_neigh = alter$neighbours,
                   alt_neigh = alter$alter4_neighbours,
                   ego_using_fp = alter$current_method,
                   alt_using_fp = alter$alter4_using_fp,
                   ego_know_asha = alter$know_asha,
                   ego_know_anm = alter$know_anm,
                   ego_know_aww = alter$know_aww,
                   ego_know_shg = alter$know_shg,
                   ego_know_pra = alter$know_pradhan,
                   ego_know_pha = alter$know_pharmacist,
                   ego_know_doc = alter$know_doctor,
                   ego_know_rel = alter$know_religious_leader,
                   alt_know_asha = NA,
                   alt_know_anm = NA,
                   alt_know_aww = NA,
                   alt_know_shg = NA,
                   alt_know_pra = NA,
                   alt_know_pha = NA,
                   alt_know_doc = NA,
                   alt_know_rel = NA,
                   ego_sons = alter$sons,
                   ego_daughters = alter$daughters,
                   alt_sons = alter$alter4_sons,
                   alt_daughters = alter$alter4_daughters,
                   alt_residence = alter$alter4_residence,
                   alt_relationship = alter$alter4r,
                   alt_learned = alter$alter4_learned,
                   alt_encourage_fp = alter$alter4_encourage_fp,
                   alt_discuss_fp = alter$alter4_discuss_fp,
                   alt_help_ego = alter$alter4_help,
                   alt_helped_by_ego = alter$alter4_helped,
                   alt_against_advice = alter$alter4_follow_advice,
                   alt_support_no_child = alter$alter4_nochild),
            tibble(ego_id = alter$alter_id,
                   alter_name = alter$alter5,
                   ego_sex = NA,
                   alt_sex = alter$alter5_sex,
                   ego_caste = alter$caste,
                   alt_caste = alter$alter5_caste,
                   ego_edu = alter$education,
                   alt_edu = NA,
                   ego_fam = alter$family_members,
                   alt_fam = alter$alter5_family,
                   ego_friends = alter$friends,
                   alt_friends = alter$alter5_friends,
                   ego_neigh = alter$neighbours,
                   alt_neigh = alter$alter5_neighbours,
                   ego_using_fp = alter$current_method,
                   alt_using_fp = alter$alter5_using_fp,
                   ego_know_asha = alter$know_asha,
                   ego_know_anm = alter$know_anm,
                   ego_know_aww = alter$know_aww,
                   ego_know_shg = alter$know_shg,
                   ego_know_pra = alter$know_pradhan,
                   ego_know_pha = alter$know_pharmacist,
                   ego_know_doc = alter$know_doctor,
                   ego_know_rel = alter$know_religious_leader,
                   alt_know_asha = NA,
                   alt_know_anm = NA,
                   alt_know_aww = NA,
                   alt_know_shg = NA,
                   alt_know_pra = NA,
                   alt_know_pha = NA,
                   alt_know_doc = NA,
                   alt_know_rel = NA,
                   ego_sons = alter$sons,
                   ego_daughters = alter$daughters,
                   alt_sons = alter$alter5_sons,
                   alt_daughters = alter$alter5_daughters,
                   alt_residence = alter$alter5_residence,
                   alt_relationship = alter$alter5r,
                   alt_learned = alter$alter5_learned,
                   alt_encourage_fp = alter$alter5_encourage_fp,
                   alt_discuss_fp = alter$alter5_discuss_fp,
                   alt_help_ego = alter$alter5_help,
                   alt_helped_by_ego = alter$alter5_helped,
                   alt_against_advice = alter$alter5_follow_advice,
                   alt_support_no_child = alter$alter5_nochild))

# drop rows for missing alters
ea %<>% filter(is.na(alter_name) == F)

##############
### GENDER ###
##############

# check unique values
# unique(ea$ego_sex)
# unique(ea$alt_sex)

# need to get sex from ego survey
for(i in 1:NROW(ea)){
  ea$ego_sex[i] <- ego_alter_old$alt_sex[ego_alter_old$alter_id == ea$ego_id[i]]
}

# check unique values
# unique(ea$ego_sex)
# unique(ea$alt_sex)

# set to numeric
ea$ego_sex <- as.numeric(ea$ego_sex)
ea$alt_sex <- as.numeric(ea$alt_sex)

# check unique values
# unique(ea$ego_sex)
# unique(ea$alt_sex)

# summarise
sex <- ea$ego_sex == ea$alt_sex
dat <- tabyl(sex) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# create homophily output
homo_alt <- tibble(metric = 'Gender (%)',
               value = dat %>% filter(sex == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(sex == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(sex == 'TRUE') %>% select(n) +
                           dat %>% filter(sex == 'FALSE') %>% select(n)))

#############
### CASTE ###
#############

# check unique values
# unique(ea$ego_caste)
# unique(ea$alt_caste)

# set to numeric
ea$ego_caste <- as.numeric(ea$ego_caste)
ea$alt_caste <- as.numeric(ea$alt_caste)

# set don't know to NA
ea$alt_caste[ea$alt_caste == 9] <- NA

# summarise
caste <- ea$ego_caste == ea$alt_caste
dat <- tabyl(caste) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# create homophily output
homo_alt %<>% add_row(metric = 'Caste (%)',
               value = dat %>% filter(caste == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(caste == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(caste == 'TRUE') %>% select(n) +
                           dat %>% filter(caste == 'FALSE') %>% select(n)))

#################
### EDUCATION ###
#################

# DON'T HAVE AALTER EDUCATION FROM ALTER SURVEY !!!

################################
### NUMBER OF FAMILY MEMBERS ###
################################

# check unique values
# unique(ea$ego_fam)
# unique(ea$alt_fam)

# convert to numeric
ea$ego_fam <- as.numeric(ea$ego_fam)
ea$alt_fam <- as.numeric(ea$alt_fam)

# set don't know to NA
ea$alt_fam[ea$alt_fam == 99] <- NA

# calculate bias homophily
# fam <- ea$ego_fam - ea$alt_fam
# fam <- tibble(mean_fam = mean(fam, na.rm = T),
#               med_fam = median(fam, na.rm = T),
#               n = length(fam[is.na(fam) == F]))
# 
# write.csv(fam, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/homophily/alt_fam_bias.csv',
#           row.names = F)

# create formula to calculate sd homophily
homo_sd <- function(ego, alt){
  out <- alt - ego
  out <- out*out
  n <- length(out[is.na(out) == F])
  out <- sum(out, na.rm = T)
  out <- out/n
  return(c(round(sqrt(out), 2), n))
}

# calculate sd homophily
fam_sd <- homo_sd(ea$ego_fam, ea$alt_fam)
dat <- tibble(aed = fam_sd[1],
                 n = fam_sd[2])

# add to homophily output
homo_alt %<>% add_row(metric = 'Number of Family Members (AED)',
               value = dat %>% select(aed) %>% as.character,
               N = dat %>% select(n) %>% as.character)

#######################################
### NUMBER OF FRIENDS AND NEIGHBORS ###
#######################################

# check unique values
# unique(ea$ego_friends)
# unique(ea$alt_friends)
# unique(ea$ego_neigh)
# unique(ea$alt_neigh)

# convert to numeric
ea$ego_friends <- as.numeric(ea$ego_friends)
ea$alt_friends <- as.numeric(ea$alt_friends)
ea$ego_neigh <- as.numeric(ea$ego_neigh)
ea$alt_neigh <- as.numeric(ea$alt_neigh)

# set don't know to NA
ea$alt_friends[ea$alt_friends == 99] <- NA
ea$alt_neigh[ea$alt_neigh == 99] <- NA

# # calculate homophily
# friends <- ea$ego_friends - ea$alt_friends
# neigh <- ea$ego_neigh - ea$alt_neigh
# friends_neigh <- (ea$ego_friends + ea$ego_neigh) - (ea$alt_friends + ea$alt_neigh)
# 
# friends_neigh <- tibble(mean_friends = mean(friends, na.rm = T),
#                         med_friends = median(friends, na.rm = T),
#                         n_friends = length(friends[is.na(friends) == F]),
#                         mean_neigh = mean(neigh, na.rm = T),
#                         med_neigh = median(neigh, na.rm = T),
#                         n_neigh = length(neigh[is.na(neigh) == F]),
#                         mean_friends_neigh = mean(friends_neigh, na.rm = T),
#                         med_friends_neigh = median(friends_neigh, na.rm = T),
#                         n_friends_neigh = length(friends_neigh[is.na(friends_neigh) == F]))

# calculate sd homophily
friends_sd <- homo_sd(ea$ego_friends, ea$alt_friends)
neigh_sd <- homo_sd(ea$ego_neigh, ea$alt_neigh)
friends_neigh_sd <- homo_sd((ea$ego_friends + ea$ego_neigh), (ea$alt_friends + ea$alt_neigh))
dat <- tibble(aed_friends = friends_sd[1],
                               n_friends = friends_sd[2],
                               aed_neigh = neigh_sd[1],
                               n_neigh = neigh_sd[2],
                               aed_friends_neigh = friends_neigh_sd[1],
                               n_friends_neigh = friends_neigh_sd[2])

# add to homophily output
homo_alt %<>% add_row(metric = 'Number of Friends (AED)',
               value = dat %>% select(aed_friends) %>% as.character,
               N = dat %>% select(n_friends) %>% as.character) %>%
  add_row(metric = 'Number of Neighbors (AED)',
               value = dat %>% select(aed_neigh) %>% as.character,
               N = dat %>% select(n_neigh) %>% as.character) %>%
  add_row(metric = 'Number of Friends & Neighbors Combined (AED)',
               value = dat %>% select(aed_friends_neigh) %>% as.character,
               N = dat %>% select(n_friends_neigh) %>% as.character)

#####################
### PRACTICING FP ###
#####################

# alt values
# 1 = Yes, 2 = No, 3 = menopause (need to switch to NA)

# alt values
# 1 = Yes, 2 = No, 9 = Don't Know

# check unique values
# unique(ea$ego_using_fp)
# unique(ea$alt_using_fp)

# set values to numeric
ea$ego_using_fp <- as.numeric(ea$ego_using_fp)
ea$alt_using_fp <- as.numeric(ea$alt_using_fp)

# if alter is husband or wife change to same value as ego
# fix issue with 1 NA value
husband <- str_detect(ea$alt_relationship, 'Husband')
husband[is.na(husband)] <- FALSE

ea$alt_using_fp[husband] <- ea$ego_using_fp[husband]

# set don't know to NA
ea$alt_using_fp[ea$alt_using_fp == 9] <- NA

# calculate homophily
using_fp <- ea$ego_using_fp == ea$alt_using_fp
dat <- tabyl(using_fp) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo_alt %<>% add_row(metric = 'Currently Using Family Planning (%)',
               value = dat %>% filter(using_fp == 'TRUE') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(using_fp == 'TRUE') %>% select(n),
                         '/',
                         dat %>% filter(using_fp == 'TRUE') %>% select(n) +
                           dat %>% filter(using_fp == 'FALSE') %>% select(n)))



##########################
### NUMBER OF CHILDREN ###
##########################

# check unique values
# unique(ea$ego_sons)
# unique(ea$alt_sons)
# unique(ea$ego_daughters)
# unique(ea$alt_daughters)

# convert to numeric
ea$ego_sons <- as.numeric(ea$ego_sons)
ea$alt_sons <- as.numeric(ea$alt_sons)
ea$ego_daughters <- as.numeric(ea$ego_daughters)
ea$alt_daughters <- as.numeric(ea$alt_daughters)

# if alter is husband or wife change to same value as ego
# fix issue with 1 NA value
husband <- str_detect(ea$alt_relationship, 'Husband')
husband[is.na(husband)] <- FALSE

ea$alt_sons[husband] <- ea$ego_sons[husband]
ea$alt_daughters[husband] <- ea$ego_daughters[husband]

# set don't know to NA
ea$alt_sons[ea$alt_sons == 99] <- NA
ea$alt_daughters[ea$alt_daughters == 99] <- NA

# calculate bias homophily
# sons <- ea$ego_sons - ea$alt_sons
# daughters <- ea$ego_daughters - ea$alt_daughters
# children <- (ea$ego_sons + ea$ego_daughters) - (ea$alt_sons + ea$alt_daughters)
# 
# children_bias <- tibble(mean_sons = mean(sons, na.rm = T),
#                         med_sons = median(sons, na.rm = T),
#                         n_sons = length(sons[is.na(sons) == F]),
#                         mean_daughters = mean(daughters, na.rm = T),
#                         med_daughters = median(daughters, na.rm = T),
#                         n_daughters = length(neigh[is.na(daughters) == F]),
#                         mean_children = mean(children, na.rm = T),
#                         med_children = median(children, na.rm = T),
#                         n_children = length(children[is.na(children) == F]))

# calculate sd homophily
sons_sd <- homo_sd(ea$ego_sons, ea$alt_sons)
daughters_sd <- homo_sd(ea$ego_daughters, ea$alt_daughters)
children_sd <- homo_sd((ea$ego_sons + ea$ego_daughters), (ea$alt_sons + ea$alt_daughters))
dat <- tibble(aed_sons = sons_sd[1],
                               n_sons = sons_sd[2],
                               aed_daughters = daughters_sd[1],
                               n_daughters = daughters_sd[2],
                               aed_children = children_sd[1],
                               n_children = children_sd[2])

# add to homophily output
homo_alt %<>% add_row(metric = 'Number of Sons (AED)',
               value = dat %>% select(aed_sons) %>% as.character,
               N = dat %>% select(n_sons) %>% as.character) %>%
  add_row(metric = 'Number of Daughters (AED)',
               value = dat %>% select(aed_daughters) %>% as.character,
               N = dat %>% select(n_daughters) %>% as.character) %>%
  add_row(metric = 'Number of Children Total (AED)',
               value = dat %>% select(aed_children) %>% as.character,
               N = dat %>% select(n_children) %>% as.character)

##############################################
### BASIC PROPORTION OF PLACE OF RESIDENCE ###
##############################################

# check unique values
# unique(ea$alt_residence)

# recode values
ea %<>% mutate(alt_residence = recode(alt_residence, 
                                     '1' = 'Same Household',
                                     '2' = 'Same Village',
                                     '3' = 'Another Village (same district)',
                                     '4' = 'Outside this District'))

# build tabyl
dat <- ea %>% tabyl(alt_residence) %>%
  adorn_pct_formatting(digits = 2)

# if valid percent remove percent and change name of valid percent
if('valid_percent' %in% colnames(dat)){
  dat %<>% select(-percent) %>% rename(percent = valid_percent)
}

# add to homophily output
homo_alt %<>% add_row(metric = 'Live in Same Household (%)',
               value = dat %>% filter(alt_residence == 'Same Household') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(alt_residence == 'Same Household') %>% select(n),
                         '/',
                         dat %>% select(n) %>% sum)) %>%
  add_row(metric = 'Live in Same Village (%)',
               value = dat %>% filter(alt_residence == 'Same Village') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(alt_residence == 'Same Village') %>% select(n),
                         '/',
                         dat %>% select(n) %>% sum)) %>%
  add_row(metric = 'Live in Another Village, Same District (%)',
               value = dat %>% filter(alt_residence == 'Another Village (same district)') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(alt_residence == 'Another Village (same district)') %>% select(n),
                         '/',
                         dat %>% select(n) %>% sum)) %>%
  add_row(metric = 'Live in Another District (%)',
               value = dat %>% filter(alt_residence == 'Outside this District') %>% select(percent) %>% as.character,
               N = str_c(dat %>% filter(alt_residence == 'Outside this District') %>% select(n),
                         '/',
                         dat %>% select(n) %>% sum))

```

```{r, echo = F, warning = F, message = F, results = 'asis'}

###########################################
### HETEROGENEITY OF ALTERS AND AALTERS ###
###########################################

###########
### SEX ###
###########

# check unique values
# unique(ea$alt_sex)

# build proportions
sex <- ea %>% tabyl(alt_sex)

# create a function to calculate blaus and iqv
blau <- function(perc){
  b <- perc*perc
  k <- length(perc)
  b <- (1 - sum(b)) %>% round(2)
  iqv <- (b / (1-(1/k))) %>% round(2)
  return(c(b, iqv, k))
}

if('valid_percent' %in% colnames(sex)){
  sex %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- sex$n[is.na(sex$percent) == F] %>% sum

# calculate heterogeneity
sex <- blau(na.omit(sex$percent))

# create tibble
dat = tibble(blau = sex[1],
             iqv = sex[2],
             k = sex[3])

# create heterogeneity output
hetero_alt <- tibble(metric = 'Gender',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

#############
### CASTE ###
#############

# check unique values
# unique(ea$alt_caste)

# build proportions
caste <- ea %>% tabyl(alt_caste)

if('valid_percent' %in% colnames(caste)){
  caste %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- caste$n[is.na(caste$percent) == F] %>% sum

# calculate heterogeneity
caste <- blau(na.omit(caste$percent))

# create tibble
dat = tibble(blau = caste[1],
              iqv = caste[2],
               k = caste[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Caste',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

################################
### NUMBER OF FAMILY MEMBERS ###
################################

# check unique values
# unique(ea$alt_fam)

# # calculate heterogeneity
# fam <- tibble(fam_sd = sd(ea$alt_fam, na.rm = T) %>% round(2),
#               n = length(ea$alt_fam[is.na(ea$alt_fam) == F]))

#######################################
### NUMBER OF FRIENDS AND NEIGHBORS ###
#######################################

# check unique values
# unique(ea$alt_friends)
# unique(ea$alt_neigh)

# # calculate heterogeneity
# friends_neigh <- tibble(friends_sd = sd(ea$alt_friends, na.rm = T) %>% round(2),
#               friends_n = length(ea$alt_friends[is.na(ea$alt_friends) == F]),
#               neigh_sd = sd(ea$alt_neigh, na.rm = T) %>% round(2),
#               neigh_n = length(ea$alt_neigh[is.na(ea$alt_neigh) == F]),
#               friends_neigh_sd = sd((ea$alt_friends + ea$alt_neigh), na.rm = T) %>% round(2),
#               friends_neigh_n = length((ea$alt_friends + ea$alt_neigh)[is.na((ea$alt_friends + ea$alt_neigh)) == F]))

#####################
### PRACTICING FP ###
#####################

# PC ego values
# 1 = Yes, 2 = No

# alt values
# 1 = Yes, 2 = No, 9 = Don't Know

# check unique values
# unique(ea$alt_using_fp)

# calculate heterogeneity
using_fp <- tabyl(ea$alt_using_fp)

if('valid_percent' %in% colnames(using_fp)){
  using_fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- using_fp$n[is.na(using_fp$percent) == F] %>% sum
using_fp <- blau(na.omit(using_fp$percent))
dat <- tibble(blau = using_fp[1],
                   iqv = using_fp[2],
                   k = using_fp[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Currently Using Family Planning',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

###############################
### PEOPLE KNOWN IN VILLAGE ###
###############################

# # check some values
# unique(ea$alt_know_asha)
# 
# # for ego, 1 is Yes, 2 is heard, 9 is don't know/haven't heard
# # for alter 1 is Yes, 2 is No, 9 is not sure
# # we should change ego values of 9 to 2 to match alter
# # remove alter rows with 9
# 
# # calculate heterogeneity
# ppl <- tabyl(ea$alt_know_asha)
# ppl <- blau(na.omit(ppl$valid_percent))
# ppl <- tibble(know_asha_blau = ppl[1],
#               know_asha_iqv = ppl[2],
#               k = ppl[3])
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/heterogeneity/ego_know_asha.csv',
#           row.names = F)
# 
# # anm
# # calculate heterogeneity
# ppl <- tabyl(ea$alt_know_anm)
# ppl <- blau(na.omit(ppl$valid_percent))
# ppl <- tibble(know_anm_blau = ppl[1],
#               know_anm_iqv = ppl[2],
#               k = ppl[3])
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/heterogeneity/ego_know_anm.csv',
#           row.names = F)
# 
# # aww
# # calculate heterogeneity
# ppl <- tabyl(ea$alt_know_aww)
# ppl <- blau(na.omit(ppl$valid_percent))
# ppl <- tibble(know_aww_blau = ppl[1],
#               know_aww_iqv = ppl[2],
#               k = ppl[3])
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/heterogeneity/ego_know_aww.csv',
#           row.names = F)
# 
# # shg
# # calculate heterogeneity
# ppl <- tabyl(ea$alt_know_shg)
# ppl <- blau(na.omit(ppl$valid_percent))
# ppl <- tibble(know_shg_blau = ppl[1],
#               know_shg_iqv = ppl[2],
#               k = ppl[3])
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/heterogeneity/ego_know_shg.csv',
#           row.names = F)
# 
# # pradhan
# # calculate heterogeneity
# ppl <- tabyl(ea$alt_know_pra)
# ppl <- blau(na.omit(ppl$valid_percent))
# ppl <- tibble(know_pra_blau = ppl[1],
#               know_pra_iqv = ppl[2],
#               k = ppl[3])
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/heterogeneity/ego_know_pradhan.csv',
#           row.names = F)
# 
# # pharmacist
# # calculate heterogeneity
# ppl <- tabyl(ea$alt_know_pha)
# ppl <- blau(na.omit(ppl$valid_percent))
# ppl <- tibble(know_pha_blau = ppl[1],
#               know_pha_iqv = ppl[2],
#               k = ppl[3])
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/heterogeneity/ego_know_pha.csv',
#           row.names = F)
# 
# # doctor
# # calculate heterogeneity
# ppl <- tabyl(ea$alt_know_doc)
# ppl <- blau(na.omit(ppl$valid_percent))
# ppl <- tibble(know_doc_blau = ppl[1],
#               know_doc_iqv = ppl[2],
#               k = ppl[3])
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/heterogeneity/ego_know_doctor.csv',
#           row.names = F)
# 
# # religious leader
# # calculate heterogeneity
# ppl <- tabyl(ea$alt_know_rel)
# ppl <- blau(na.omit(ppl$valid_percent))
# ppl <- tibble(know_rel_blau = ppl[1],
#               know_rel_iqv = ppl[2],
#               k = ppl[3])
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/heterogeneity/ego_know_rel.csv',
#           row.names = F)
# 
# # calculate health worker category
# 
# 
# # calculate homophily
# # calculate heterogeneity
# ppl <- tabyl(alt_hw)
# ppl <- blau(na.omit(ppl$percent))
# ppl <- tibble(know_hw_blau = ppl[1],
#               know_hw_iqv = ppl[2],
#               k = ppl[3])
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/heterogeneity/ego_know_health_worker.csv',
#           row.names = F)
# 
# # calculate village leader category
# # calculate heterogeneity
# ppl <- tabyl(alt_vl)
# ppl <- blau(na.omit(ppl$percent))
# ppl <- tibble(know_vl_blau = ppl[1],
#               know_vl_iqv = ppl[2],
#               k = ppl[3])
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/heterogeneity/ego_know_village_leader.csv',
#           row.names = F)
# 
# # now total number of people
# # calculate heterogeneity
# ppl <- tibble(ppl_known_village_sd = sd(alt_ppl, na.rm = T) %>% round(2),
#               n = length(alt_ppl[is.na(alt_ppl) == F]))
# 
# write.csv(ppl, 
#           '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/heterogeneity/ego_ppl_known_village.csv',
#           row.names = F)

##########################
### NUMBER OF CHILDREN ###
##########################

# check unique values
# unique(ea$alt_sons)
# unique(ea$alt_daughters)

# # calculate heterogeneity
# children <- tibble(sons_sd = sd(ea$alt_sons, na.rm = T) %>% round(2),
#               sons_n = length(ea$alt_sons[is.na(ea$alt_sons) == F]),
#               daughters_sd = sd(ea$alt_daughters, na.rm = T) %>% round(2),
#               daughters_n = length(ea$alt_daughters[is.na(ea$alt_daughters) == F]),
#               children_sd = sd((ea$alt_sons + ea$alt_daughters), na.rm = T) %>% round(2),
#               children_n = length((ea$alt_sons + ea$alt_daughters)[is.na((ea$alt_sons + ea$alt_daughters)) == F]))

##########################
### PLACE OF RESIDENCE ###
##########################

# check unique values
# unique(ea$alt_residence)

# calculate heterogeneity
res <- tabyl(ea$alt_residence)

if('valid_percent' %in% colnames(res)){
  res %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- res$n[is.na(res$percent) == F] %>% sum
res <- blau(na.omit(res$percent))
dat <- tibble(blau = res[1],
              iqv = res[2],
              k = res[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Residence',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

#######################
### SOCIAL LEARNING ###
#######################

# check unique values
#unique(ea$alt_learned)

# calculate homophily
a <- tabyl(str_detect(ea$alt_learned, "A"))

if('valid_percent' %in% colnames(a)){
  a %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- a$n[is.na(a$percent) == F] %>% sum
a <- blau(na.omit(a$percent))
dat <- tibble(blau = a[1],
              iqv = a[2],
              k = a[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Social Learning: Get along with family',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

b <- tabyl(str_detect(ea$alt_learned, "B"))

if('valid_percent' %in% colnames(b)){
  b %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- b$n[is.na(b$percent) == F] %>% sum
b <- blau(na.omit(b$percent))
dat <- tibble(blau = b[1],
              iqv = b[2],
              k = b[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Social Learning: Ways of earning',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

c <- tabyl(str_detect(ea$alt_learned, "C"))

if('valid_percent' %in% colnames(c)){
  c %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- c$n[is.na(c$percent) == F] %>% sum
c <- blau(na.omit(c$percent))
dat <- tibble(blau = c[1],
              iqv = c[2],
              k = c[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Social Learning: Take care of children',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

d <- tabyl(str_detect(ea$alt_learned, "D"))

if('valid_percent' %in% colnames(d)){
  d %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- d$n[is.na(d$percent) == F] %>% sum
d <- blau(na.omit(d$percent))
dat <- tibble(blau = d[1],
              iqv = d[2],
              k = d[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Social Learning: Get health care',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

e <- tabyl(str_detect(ea$alt_learned, "E"))

if('valid_percent' %in% colnames(e)){
  e %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- e$n[is.na(e$percent) == F] %>% sum
e <- blau(na.omit(e$percent))
dat <- tibble(blau = e[1],
              iqv = e[2],
              k = e[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Social Learning: Apply for government schemes',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

f <- tabyl(str_detect(ea$alt_learned, "F"))

if('valid_percent' %in% colnames(f)){
  f %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- f$n[is.na(f$percent) == F] %>% sum
f <- blau(na.omit(f$percent))
dat <- tibble(blau = f[1],
              iqv = f[2],
              k = f[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Social Learning: Plan no. of children to have',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

g <- tabyl(str_detect(ea$alt_learned, "G"))

if('valid_percent' %in% colnames(g)){
  g %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- g$n[is.na(g$percent) == F] %>% sum
g <- blau(na.omit(g$percent))
dat <- tibble(blau = g[1],
              iqv = g[2],
              k = g[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Social Learning: FP methods',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

###########################
### ENCOURAGE USE OF FP ###
###########################

# check unique values
# unique(ea$alt_encourage_fp)

# calculate heterogeneity
fp <- tabyl(ea$alt_encourage_fp)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
             iqv = fp[2],
              k = fp[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Encourage Use of Family Planning',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

#################################
### DISCUSS FP METHODS FREELY ###
#################################

# check unique values
# unique(ea$alt_discuss_fp)

# calculate heterogeneity
fp <- tabyl(ea$alt_discuss_fp)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
             iqv = fp[2],
              k = fp[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Discuss FP Methods Freely',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

###########################
### ALT HELP/ADVISE EGO ###
###########################

# check unique values
# unique(ea$alt_help_ego)

# calculate heterogeneity
fp <- tabyl(ea$alt_help_ego)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
             iqv = fp[2],
              k = fp[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = "Alter's Alter Help/Advise Alter",
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

###########################
### EGO HELP/ADVISE ALT ###
###########################

# check unique values
# unique(ea$alt_helped_by_ego)

# calculate heterogeneity
fp <- tabyl(ea$alt_helped_by_ego)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
             iqv = fp[2],
              k = fp[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = "Alter Help/Advise Alter's Alter",
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

############################
### GOING AGAINST ADVICE ###
############################

# check unique values
#unique(ea$alt_against_advice)

# calculate heterogeneity
fp <- tabyl(ea$alt_against_advice)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
             iqv = fp[2],
              k = fp[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Going Against Advise',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)

###################################
### SUPPORT NOT HAVING CHILDREN ###
###################################

# check unique values
#unique(ea$alt_support_no_child)

# calculate heterogeneity
fp <- tabyl(ea$alt_support_no_child)

if('valid_percent' %in% colnames(fp)){
  fp %<>% select(-percent) %>% rename(percent = valid_percent)
}

n <- fp$n[is.na(fp$percent) == F] %>% sum
fp <- blau(na.omit(fp$percent))
dat <- tibble(blau = fp[1],
             iqv = fp[2],
              k = fp[3])

# add to heterogeneity output
hetero_alt %<>% add_row(metric = 'Support Not Having Children',
               blau_index = dat %>% select(blau) %>% as.character,
               iqv = dat %>% select(iqv) %>% as.character,
               k = dat %>% select(k) %>% as.character,
               n = n %>% as.character)


```

# 2. Homophily
## A) Ego and Alter

```{r, echo = F, warning = F, message = F, results = 'asis'}
# print homophily output
homo %>%
  kbl(caption = 'Homophily Between Ego and Alter (AED = Average Euclidean Distance)') %>%
  kable_classic_2('hover', full_width = F, position = 'left')
```

## B) Alter and Alter's Alter

```{r, echo = F, warning = F, message = F, results = 'asis'}
# print homophily output
homo_alt %>%
  kbl(caption = "Homophily Between Alter's Alter and Alter (AED = Average Euclidean Distance)") %>%
  kable_classic_2('hover', full_width = F, position = 'left')
```

# 3. Heterogeneity
## A) Between Alters (Ego's Perspective)

```{r, echo = F, warning = F, message = F, results = 'asis'}
# print heterogeneity output
hetero %>%
  kbl(caption = "Heterogeneity Between Alters (Ego's Perspective)") %>%
  kable_classic_2('hover', full_width = F, position = 'left')
```

## B) Between Alter's Alters (Alter's Perspective)

```{r, echo = F, warning = F, message = F, results = 'asis'}
# print heterogeneity output
hetero_alt %>%
  kbl(caption = "Heterogeneity Between Alter's Alters (Alters Perspective)") %>%
  kable_classic_2('hover', full_width = F, position = 'left')
```

# 4. Tie Strength and Intensity
## A) Ego and Alters

```{r, echo = F, warning = F, message = F, results = 'asis'}

# this code loads csv data of ego and alter interviews
# and calculates tie intensity and strength

# load packages
library(magrittr)
library(egor)
library(janitor)
library(tidyverse)
library(readxl)
library(igraph)
library(readstata13)

#########################################
### LOAD EGO AND ALTER DATA AND CLEAN ###
#########################################

# load ego and alter cleaned data
ego <- read_excel(path = ego_data_f)

alter <-read_excel(path = alter_data_f)

# load pc data
ego_pc <- read_excel(path = ego_pc_f)

# load list of duplicate ids
dup_id <- read_excel(path = dup_id_f)

# remove first row with 'qe' names
ego <- ego[-1,]
alter <- alter[-1,]

# clean column names only keep part after last "."
ego_names <- sapply(colnames(ego), FUN = function(x){
  st <- str_split(x, pattern = glob2rx("*-*"))
  st <- st[[1]][length(st[[1]])]
  return(st)
})

names(ego_names) <- NULL
colnames(ego) <- ego_names

alter_names <- sapply(colnames(alter), FUN = function(x){
  st <- str_split(x, pattern = glob2rx("*-*"))
  st <- st[[1]][length(st[[1]])]
  return(st)
})

names(alter_names) <- NULL
colnames(alter) <- alter_names

rm(ego_names, alter_names)

# remove empty columns from "notes"
ego <- ego[,str_detect(colnames(ego), 'note') == F]
alter <- alter[,str_detect(colnames(alter), 'note') == F]

# replace character NA values with NA
ego[ego == "NA"] <- NA
alter[alter == "NA"] <- NA

# fix district, block and village in alter data
alter$district_name <- alter$`district name_clean`
alter$block_name <- alter$`block name_clean`
alter$village_name <- alter$`village name_clean`

# remove "clean" columns
alter <- alter %>% select(-c(`district name_clean`, `block name_clean`, `village name_clean`))

# add alter-alter tie columns to ego dataset so we can build edgelist below
# let's first extract the correct question so easier to look at
alter_know <- ego[,str_detect(colnames(ego), glob2rx('alter?_know?'))]

# set to numeric
alter_know <- sapply(alter_know, as.numeric)

# set "don't know" to 0 since then tie won't exist. both responses labeled 2 and 9
alter_know[alter_know == 2] <- 0
alter_know[alter_know == 9] <- 0

# create new df with only a single column for combinations
alter_know %<>% as.data.frame %>% 
  mutate(know12 = alter1_know2 + alter2_know1,
         know13 = alter1_know3 + alter3_know1,
         know14 = alter1_know4 + alter4_know1,
         know15 = alter1_know5 + alter5_know1,
         know23 = alter2_know3 + alter3_know2,
         know24 = alter2_know4 + alter4_know2,
         know25 = alter2_know5 + alter5_know2,
         know34 = alter3_know4 + alter4_know3,
         know35 = alter3_know5 + alter5_know3,
         know45 = alter4_know5 + alter5_know4)

# now set 0 to NA since we just want to identify tie or not
alter_know %<>% select(know12:know45)
alter_know[alter_know == 0] <- NA

# add simple know columns back into ego df
ego %<>% add_column(alter_know)
rm(alter_know)

# add aalter-aalter tie columns to alter dataset so we can build edgelist below
# let's first extract the correct question so easier to look at
alter_know <- alter[,str_detect(colnames(alter), glob2rx('alter?_know?'))]

# set to numeric
alter_know <- sapply(alter_know, as.numeric)

# set "don't know" to 0 since then tie won't exist. both responses labeled 2 and 9
alter_know[alter_know == 2] <- 0
alter_know[alter_know == 9] <- 0

# create new df with only a single column for combinations
alter_know %<>% as.data.frame %>% 
  mutate(know12 = alter1_know2 + alter2_know1,
         know13 = alter1_know3 + alter3_know1,
         know14 = alter1_know4 + alter4_know1,
         know15 = alter1_know5 + alter5_know1,
         know23 = alter2_know3 + alter3_know2,
         know24 = alter2_know4 + alter4_know2,
         know25 = alter2_know5 + alter5_know2,
         know34 = alter3_know4 + alter4_know3,
         know35 = alter3_know5 + alter5_know3,
         know45 = alter4_know5 + alter5_know4)

# now set 0 to NA since we just want to identify tie or not
alter_know %<>% select(know12:know45)
alter_know[alter_know == 0] <- NA

# add simple know columns back into alter df
alter %<>% add_column(alter_know)
rm(alter_know)

##########
## EGO ###
##########

######################################################
### BUILD TIBBLE OF ATTRIBUTES OF INTEREST FOR EGO ###
######################################################

# length of relationship
# talking freq
# talking freq fp
# number of different things discussed

# sort ego data and PC data by woman ID so can merge
ego %<>% arrange(woman_id)
ego_pc %<>% arrange(qe6) # qe6 is woman_id

# make sure ego_ids match
# sum(ego_pc$qe6 == ego$woman_id)

# build tibble add all alters
ego_tie <- rbind(tibble(ego_id = ego$woman_id,
                        ego_age = ego_pc$pcq102,
                        ego_age_married = ego_pc$pcq201b,
                        alter_name = ego$alter1,
                        district = ego$district_name,
                        block = ego$block_name,
                        yrs_known = ego$alter1_yrs_known,
                        talk_freq = ego$alter1_talk_freq,
                        talk_freq_fp = ego$alter1_freq_talk_fp,
                        subjects = ego$alter1_subjects,
                        subjects_other = ego$alter1_subjects_other),
               tibble(ego_id = ego$woman_id,
                      ego_age = ego_pc$pcq102,
                      ego_age_married = ego_pc$pcq201b,
                      alter_name = ego$alter2,
                      district = ego$district_name,
                      block = ego$block_name,
                      yrs_known = ego$alter2_yrs_known,
                      talk_freq = ego$alter2_talk_freq,
                      talk_freq_fp = ego$alter2_freq_talk_fp,
                      subjects = ego$alter2_subjects,
                      subjects_other = ego$alter2_subjects_other),
               tibble(ego_id = ego$woman_id,
                      ego_age = ego_pc$pcq102,
                      ego_age_married = ego_pc$pcq201b,
                      alter_name = ego$alter3,
                      district = ego$district_name,
                      block = ego$block_name,
                      yrs_known = ego$alter3_yrs_known,
                      talk_freq = ego$alter3_talk_freq,
                      talk_freq_fp = ego$alter3_freq_talk_fp,
                      subjects = ego$alter3_subjects,
                      subjects_other = ego$alter3_subjects_other),
               tibble(ego_id = ego$woman_id,
                      ego_age = ego_pc$pcq102,
                      ego_age_married = ego_pc$pcq201b,
                      alter_name = ego$alter4,
                      district = ego$district_name,
                      block = ego$block_name,
                      yrs_known = ego$alter4_yrs_known,
                      talk_freq = ego$alter4_talk_freq,
                      talk_freq_fp = ego$alter4_freq_talk_fp,
                      subjects = ego$alter4_subjects,
                      subjects_other = ego$alter4_subjects_other),
               tibble(ego_id = ego$woman_id,
                      ego_age = ego_pc$pcq102,
                      ego_age_married = ego_pc$pcq201b,
                      alter_name = ego$alter5,
                      district = ego$district_name,
                      block = ego$block_name,
                      yrs_known = ego$alter5_yrs_known,
                      talk_freq = ego$alter5_talk_freq,
                      talk_freq_fp = ego$alter5_freq_talk_fp,
                      subjects = ego$alter5_subjects,
                      subjects_other = ego$alter5_subjects_other))

# drop rows for missing alters
ego_tie %<>% filter(is.na(alter_name) == F)

##############################
### LENGTH OF RELATIONSHIP ###
##############################

# check unique values for length of relationship
# unique(ego_tie$yrs_known)

# set to numeric
ego_tie$yrs_known <- as.numeric(ego_tie$yrs_known)

# reset values of 99 based on ego age and age of marriage
ego_tie$yrs_known[ego_tie$yrs_known == 99] <- ego_tie$ego_age[ego_tie$yrs_known == 99] - ego_tie$ego_age_married[ego_tie$yrs_known == 99]

# re check unique values for length of relationship
# unique(ego_tie$yrs_known)

# calculate summary data overall
ties <- ego_tie %>% 
  summarise(mean_yrs_known = mean(yrs_known, na.rm = T),
                                 med_yrs_known = median(yrs_known, na.rm = T),
                                 mean_yrs_known_perc_age = mean(yrs_known/ego_age, na.rm = T) * 100,
                                 med_yrs_known_perc_age = median(yrs_known/ego_age, na.rm = T) * 100) %>%
  round(2)

# create output
out <- tibble(metric = 'Mean',
               value = ties %>% select(mean_yrs_known) %>% as.character,
               n = sum(is.na(ego_tie$yrs_known) == F) %>% as.character) %>%
  add_row(metric = 'Mean (% of Ego Age)',
               value = ties %>% select(mean_yrs_known_perc_age) %>% as.character,
               n = sum(is.na(ego_tie$yrs_known) == F) %>% as.character) %>%
  add_row(metric = 'Median',
               value = ties %>% select(med_yrs_known) %>% as.character,
               n = sum(is.na(ego_tie$yrs_known) == F) %>% as.character) %>%
  add_row(metric = 'Median (% of Ego Age)',
               value = ties %>% select(med_yrs_known_perc_age) %>% as.character,
               n = sum(is.na(ego_tie$yrs_known) == F) %>% as.character)

# print output
out %>%
  kbl(caption = "Length of Relationship (Years Known)") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# calculate summary data by block
ties_block <- ego_tie %>% 
  group_by(block) %>%
  summarise(district = district[1],
            mean_yrs_known = mean(yrs_known, na.rm = T),
            mean_yrs_known_perc_age = mean(yrs_known/ego_age, na.rm = T) * 100,
            med_yrs_known = median(yrs_known, na.rm = T),
            med_yrs_known_perc_age = median(yrs_known/ego_age, na.rm = T) * 100) %>%
  mutate(across(where(is.numeric), round, digits=2))

# change column names
colnames(ties_block) <- c('Block', 'District', 'Mean', 'Mean (% of Ego Age)', 'Median', 'Median (% of Ego Age)')

# print output
ties_block %>%
  kbl(caption = "Length of Relationship (Years Known) By Block") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

#################################
### TALKING FREQUENCY OVERALL ###
#################################

# check unique values for talking freq overall
# table(ego_tie$talk_freq)

# recode column
ego_tie %<>% mutate(talk_freq = recode(talk_freq, 
                                       `1` = 'intensive',
                                       `2` = 'intensive',
                                       `3` = 'intensive',
                                       `4` = 'moderate',
                                       `5` = 'moderate',
                                       `6` = 'minimal',
                                       `7` = 'minimal'))

# overall summary
talk_freq <- ego_tie %>% tabyl(talk_freq) %>%
  adorn_pct_formatting(digits = 2) %>%
  mutate(talk_freq = ordered(talk_freq, levels = c('minimal', 'moderate', 'intensive'))) %>%
  arrange(talk_freq)

# print output
talk_freq %>%
  kbl(caption = "Talk Frequency Overall") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# summary by block
talk_freq_block <- ego_tie %>% mutate(talk_freq = ordered(talk_freq, levels = c('minimal', 'moderate', 'intensive'))) %>%
  arrange(talk_freq) %>%
  tabyl(block, talk_freq) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top')

# print output
talk_freq_block %>%
  kbl(caption = "Talk Frequency Overall By Block") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

############################################
### TALKING FREQUENCY IN FAMILY PLANNING ###
############################################

# check unique values for talking freq fp
# table(ego_tie$talk_freq_fp)

# recode column
ego_tie %<>% mutate(talk_freq_fp = recode(talk_freq_fp, 
                                       `1` = 'intensive',
                                       `2` = 'intensive',
                                       `3` = 'moderate',
                                       `4` = 'moderate',
                                       `5` = 'minimal')) %>%
  mutate(talk_freq_fp = replace_na(talk_freq_fp, 'none'))

# overall summary
talk_freq_fp <- ego_tie %>% tabyl(talk_freq_fp) %>%
  adorn_pct_formatting(digits = 2) %>%
  mutate(talk_freq_fp = ordered(talk_freq_fp, levels = c('minimal', 'moderate', 'intensive', 'none'))) %>%
  arrange(talk_freq_fp)

# print output
talk_freq_fp %>%
  kbl(caption = "Talk Frequency About Family Planning") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# summary by block
talk_freq_fp_block <- ego_tie %>%
  mutate(talk_freq_fp = ordered(talk_freq_fp, levels = c('minimal', 'moderate', 'intensive', 'none'))) %>%
  arrange(talk_freq_fp) %>%
  tabyl(block, talk_freq_fp) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top')

# print output
talk_freq_fp_block %>%
  kbl(caption = "Talk Frequency About Family Planning by Block") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

#################################################
### MULTIPLEXITY NUMBER OF DIFFERENT SUBJECTS ###
#################################################

# check values of subjects
# unique(ego_tie$subjects)

# count number of subjects
num_sub <- str_split(ego_tie$subjects, ',')
num_sub <- sapply(num_sub, function(x) length(x))

# add to tibble
ego_tie$num_subjects <- num_sub

# add one if mentioned other subjects
# ego_tie$num_subjects[is.na(ego_tie$subjects_other) == F] <- ego_tie$num_subjects[is.na(ego_tie$subjects_other) == F] + 1

# overall summary
num_sub <- ego_tie %>% tabyl(num_subjects) %>%
  adorn_pct_formatting(digits = 2)

# print output
num_sub %>%
  kbl(caption = "Multiplexity (Number of Different Things Discussed)") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# summary by block
num_sub_block <- ego_tie %>% tabyl(block, num_subjects) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top')
# ego_tie %>% split(.$block) %>% map(~map(.x %>% select(num_subjects), tabyl))

# print output
num_sub_block %>%
  kbl(caption = "Multiplexity (Number of Different Things Discussed) By Block") %>%
  kable_classic_2('hover', full_width = F, position = 'left')
```

## B) Alter and Alter's Alters

```{r, echo = F, warning = F, message = F, results = 'asis'}
############
## ALTER ###
############

########################################################
### BUILD TIBBLE OF ATTRIBUTES OF INTEREST FOR ALTER ###
########################################################

# length of relationship
# talking freq
# talking freq fp
# number of different things discussed

# build tibble add all aalters
alter_tie <- rbind(tibble(alter_id = alter$alter_id,
                        alter_age = alter$age,
                        aalter_name = alter$alter1,
                        district = alter$district_name,
                        block = alter$block_name,
                        yrs_known = alter$alter1_yrs_known,
                        talk_freq = alter$alter1_talk_freq,
                        talk_freq_fp = alter$alter1_freq_talk_fp,
                        subjects = alter$alter1_subjects,
                        subjects_other = alter$alter1_subjects_other),
                   tibble(alter_id = alter$alter_id,
                          alter_age = alter$age,
                          aalter_name = alter$alter2,
                          district = alter$district_name,
                          block = alter$block_name,
                          yrs_known = alter$alter2_yrs_known,
                          talk_freq = alter$alter2_talk_freq,
                          talk_freq_fp = alter$alter2_freq_talk_fp,
                          subjects = alter$alter2_subjects,
                          subjects_other = alter$alter2_subjects_other),
                   tibble(alter_id = alter$alter_id,
                          alter_age = alter$age,
                          aalter_name = alter$alter3,
                          district = alter$district_name,
                          block = alter$block_name,
                          yrs_known = alter$alter3_yrs_known,
                          talk_freq = alter$alter3_talk_freq,
                          talk_freq_fp = alter$alter3_freq_talk_fp,
                          subjects = alter$alter3_subjects,
                          subjects_other = alter$alter3_subjects_other),
                   tibble(alter_id = alter$alter_id,
                          alter_age = alter$age,
                          aalter_name = alter$alter4,
                          district = alter$district_name,
                          block = alter$block_name,
                          yrs_known = alter$alter4_yrs_known,
                          talk_freq = alter$alter4_talk_freq,
                          talk_freq_fp = alter$alter4_freq_talk_fp,
                          subjects = alter$alter4_subjects,
                          subjects_other = alter$alter4_subjects_other),
                   tibble(alter_id = alter$alter_id,
                          alter_age = alter$age,
                          aalter_name = alter$alter5,
                          district = alter$district_name,
                          block = alter$block_name,
                          yrs_known = alter$alter5_yrs_known,
                          talk_freq = alter$alter5_talk_freq,
                          talk_freq_fp = alter$alter5_freq_talk_fp,
                          subjects = alter$alter5_subjects,
                          subjects_other = alter$alter5_subjects_other))

# drop rows for missing alters
alter_tie %<>% filter(is.na(aalter_name) == F)

# drop rows for incomplete surveys
alter_tie %<>% filter(is.na(yrs_known) == F)

##############################
### LENGTH OF RELATIONSHIP ###
##############################

# check unique values for length of relationship
# unique(alter_tie$yrs_known)

# set to numeric
alter_tie$yrs_known <- as.numeric(alter_tie$yrs_known)

# reset values of 99 based on alter age and age of marriage
# we don't have alter age of marriage!!!
# ego_tie$yrs_known[ego_tie$yrs_known == 99] <- ego_tie$ego_age[ego_tie$yrs_known == 99] - ego_tie$ego_age_married[ego_tie$yrs_known == 99]

# re check unique values for length of relationship
# unique(alter_tie$yrs_known)

# # calculate summary data overall
# ties <- alter_tie %>% 
#   summarise(mean_yrs_known = mean(yrs_known, na.rm = T),
#             med_yrs_known = median(yrs_known, na.rm = T))
# 
# write.csv(ties, '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/tie_strength_intensity/ego_yrs_known.csv',
#           row.names = F)
# 
# # calculate summary data by block
# ties_block <- ego_tie %>% 
#   group_by(block) %>%
#   summarise(district = district[1],
#             mean_yrs_known = mean(yrs_known, na.rm = T),
#             med_yrs_known = median(yrs_known, na.rm = T),
#             mean_yrs_known_perc_age = mean(yrs_known/ego_age, na.rm = T),
#             med_yrs_known_perc_age = median(yrs_known/ego_age, na.rm = T))
# 
# write.csv(ties_block, '/Users/bermane/Team Braintree Dropbox/ETHAN - ICRW Egocentric data Analysis/Analysis/results/tie_strength_intensity/ego_yrs_known_block.csv',
#           row.names = F)

# just show table of alter values
# ties <- alter_tie %>% tabyl(yrs_known)

```

##### We cannot calculate length of relationship in the same way because we don't have Alter's age/year married, which is necessary for cases where the response was "known since marriage" (n = ~600)

```{r, echo = F, warning = F, message = F, results = 'asis'}

#################################
### TALKING FREQUENCY OVERALL ###
#################################

# check unique values for talking freq overall
# table(alter_tie$talk_freq)

# recode column
alter_tie %<>% mutate(talk_freq = recode(talk_freq, 
                                       `1` = 'intensive',
                                       `2` = 'intensive',
                                       `3` = 'intensive',
                                       `4` = 'moderate',
                                       `5` = 'moderate',
                                       `6` = 'minimal',
                                       `7` = 'minimal'))

# overall summary
talk_freq <- alter_tie %>% tabyl(talk_freq) %>%
  adorn_pct_formatting(digits = 2) %>%
  mutate(talk_freq = ordered(talk_freq, levels = c('minimal', 'moderate', 'intensive'))) %>%
  arrange(talk_freq)

# print output
talk_freq %>%
  kbl(caption = "Talk Frequency Overall") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# summary by block
# summary by block
talk_freq_block <- alter_tie %>% mutate(talk_freq = ordered(talk_freq, levels = c('minimal', 'moderate', 'intensive'))) %>%
  arrange(talk_freq) %>%
  tabyl(block, talk_freq) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top')

# print output
talk_freq_block %>%
  kbl(caption = "Talk Frequency Overall By Block") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

############################################
### TALKING FREQUENCY IN FAMILY PLANNING ###
############################################

# check unique values for talking freq fp
# table(alter_tie$talk_freq_fp)

# recode column
alter_tie %<>% mutate(talk_freq_fp = recode(talk_freq_fp, 
                                          `1` = 'intensive',
                                          `2` = 'intensive',
                                          `3` = 'moderate',
                                          `4` = 'moderate',
                                          `5` = 'minimal')) %>%
  mutate(talk_freq_fp = replace_na(talk_freq_fp, 'none'))

# overall summary
talk_freq_fp <- alter_tie %>% tabyl(talk_freq_fp) %>%
  adorn_pct_formatting(digits = 2) %>%
  mutate(talk_freq_fp = ordered(talk_freq_fp, levels = c('minimal', 'moderate', 'intensive', 'none'))) %>%
  arrange(talk_freq_fp)

# print output
talk_freq_fp %>%
  kbl(caption = "Talk Frequency About Family Planning") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# summary by block
talk_freq_fp_block <- alter_tie %>%
  mutate(talk_freq_fp = ordered(talk_freq_fp, levels = c('minimal', 'moderate', 'intensive', 'none'))) %>%
  arrange(talk_freq_fp) %>%
  tabyl(block, talk_freq_fp) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top')

# print output
talk_freq_fp_block %>%
  kbl(caption = "Talk Frequency About Family Planning by Block") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

#################################################
### MULTIPLEXITY NUMBER OF DIFFERENT SUBJECTS ###
#################################################

# check values of subjects
# unique(alter_tie$subjects)

# count number of subjects
num_sub <- str_split(alter_tie$subjects, ',')
num_sub <- sapply(num_sub, function(x) length(x))

# add to tibble
alter_tie$num_subjects <- num_sub

# add one if mentioned other subjects
# alter_tie$num_subjects[is.na(alter_tie$subjects_other) == F] <- alter_tie$num_subjects[is.na(alter_tie$subjects_other) == F] + 1

# overall summary
num_sub <- alter_tie %>% tabyl(num_subjects) %>%
  adorn_pct_formatting(digits = 2)

# print output
num_sub %>%
  kbl(caption = "Multiplexity (Number of Different Things Discussed)") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

# summary by block
num_sub_block <- alter_tie %>% tabyl(block, num_subjects) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>% 
  adorn_title(placement = 'top')
# ego_tie %>% split(.$block) %>% map(~map(.x %>% select(num_subjects), tabyl))

# print output
num_sub_block %>%
  kbl(caption = "Multiplexity (Number of Different Things Discussed) By Block") %>%
  kable_classic_2('hover', full_width = F, position = 'left')

```
